---
title: "trial results"
author: "Allen Yeh"
output:
  html_document: default
  pdf_document: default
---

```
```

```{r warning=FALSE}
library(tidyverse)
library(gmodels)
library(rstatix)
library(ggplot2)
library(ez)

#increase print limit to 2500 values
options(max.print=3000)
```

### Import data

#### Read the csv file and claim the data type
```{r}
 
participant_id = c("1", "2", "3", "4", "5", "6", "7", "8", "9", "10", "11", "12", "13", "14", "15", "16", "17", "18", "19", "20", "21", "40", "23", "24")

key_code = c("A", "S", "D", "F", "J", "K", "L", "Semicolon")

level_code = c("full", "mediumHigh", "mediumLow", "medium", "light")
level_cols <- c("full" = "#922B21", "mediumHigh" = "#1F618D", "mediumLow" = "#1E8449", "medium" = "#1E8449", "light" = "#B7950B")

# Initialize an empty data frame
trial_log = NULL

for (x in participant_id) {
  filename <- paste("./../results/", x, ".csv", sep="")
  trial_user_log <- read_csv(filename, col_types = cols(
    id = col_factor(levels = participant_id),
    level = col_integer(),
    block = col_factor(levels = c("0", "1", "2", "3", "4", "5")),
    trial = col_integer(),
    levelCounts = col_factor(levels = c("2", "3", "4")),
    targetKey = col_factor(levels = key_code),
    targetLevel = col_factor(levels = level_code),
    pressedLevel = col_factor(levels = level_code),
    pressedRaw = col_integer(),
    isSuccessful = col_logical(),
    startTime = col_double(),
    endTime = col_double(),
    time = col_double(),
  )) %>% filter(block %in% c("1", "2", "3", "4", "5"))
  trial_log = bind_rows(trial_log,trial_user_log)
}


```

### functions

```{r warning=FALSE}
percent <- function(num, digits = 2, ...) {      
  percentage <-formatC(num * 100, format = "f", digits = digits, ...)
  
  # appending "%" symbol at the end of
  # calculate percentage value
  paste0(percentage, "%")
}

INT <- function(x){
    qnorm((rank(x) - 0.5)/length(x))
}
```

### Filter outlier with time
```{r warning = FALSE}
trial_log_filtered <- trial_log %>% 
  group_by(id, levelCounts) %>% 
  mutate(IQR = IQR(time),
            O_upper = quantile(time, probs=c( .75), na.rm = FALSE)+1.5*IQR,  
            O_lower = quantile(time, probs=c( .25), na.rm = FALSE)-1.5*IQR  
  ) %>% 
  filter(O_lower <= time & time <= O_upper)%>% 
  ungroup()
```

Total 437 trials (5.1%) got removed.

```{r warning=FALSE}
trial_log_filtered <- trial_log_filtered %>%
  filter(block != c("1"))
```

Remove the first block due to learning effect.

### Two levels
#### actual press - user threshold
```{r warning=FALSE}
log_twolevel <- trial_log_filtered %>%
  filter(levelCounts == c("2"))

log_twolevel_user <- log_twolevel %>% 
  group_by(id, targetLevel) %>% 
  mutate(
    pressRawPercent = pressedRaw * 100.0 / 255.0,
  ) %>% 
  ungroup()

log_twolevel_user_dist <- log_twolevel_user %>% 
  group_by(id, targetLevel) %>% 
  summarize(
    press_ave = sum(pressRawPercent) / n(),
    n_trials = n()
  )%>%
  ungroup()

log_twolevel_user_dist

log_twolevel_user_level_summary <- log_twolevel_user_dist  %>%
  group_by(targetLevel) %>%
  summarize(
    meanDist = press_ave %>% mean(na.rm=TRUE),
    lowCIDist = ci(press_ave)[2] %>% pmax(0),
    highCIDist = ci(press_ave)[3] %>% pmin(100),
    sdDist = ci(press_ave)[4],
    stdDist = sd(press_ave)) %>%
  ungroup() %>%
  arrange(targetLevel)

log_twolevel_user_level_summary

log_twolevel_user_quantile <- log_twolevel_user%>%
  group_by(id, targetLevel) %>%
  summarize(
    lower_outlier = boxplot.stats(pressedRaw)$stats[c(1)],
    lower = boxplot.stats(pressedRaw)$stats[c(2)],
    median = boxplot.stats(pressedRaw)$stats[c(3)],
    upper = boxplot.stats(pressedRaw)$stats[c(4)],
    upper_outlier = boxplot.stats(pressedRaw)$stats[c(5)],
  ) %>%
  ungroup() %>%
  arrange(id, targetLevel)

library(reshape2) # for dcast

melted_threshold <- melt(log_twolevel_user_quantile, id.vars = c("id", "targetLevel"), measure.vars = c("lower_outlier", "lower", "median", "upper", "upper_outlier"))

#melted_threshold

cast_threshold <- dcast(melted_threshold, id~targetLevel * variable, value.var="value")%>%
  group_by(id) %>%
  mutate(
    full_threshold = median(c(full_lower_outlier, full_lower,light_upper, light_upper_outlier)),
    full_threshold_percent = full_threshold * 100.0 / 255.0,
  ) %>%
  ungroup()

twolevel_threshold_summary <- cast_threshold  %>%
  summarize(
    meanFullThreshold = full_threshold_percent %>% mean(na.rm=TRUE),
    lowCIFullThreshold = ci(full_threshold_percent)[2] %>% pmax(0),
    highCIFullThreshold = ci(full_threshold_percent)[3],
    sdFullThreshold = ci(full_threshold_percent)[4],
    stdFullThreshold = sd(full_threshold_percent))

twolevel_threshold_summary

log_twolevel_user <- merge(log_twolevel_user, cast_threshold,
                          by = 'id', all = TRUE)

log_twolevel_user <- log_twolevel_user %>% 
  mutate(
    pressLevel_user = ifelse(pressedRaw >= full_threshold, "full", "light"),
    isSuccessful_user = (targetLevel == pressLevel_user)
  )

#log_twolevel_user


twolovel_user_press <- ggplot(log_twolevel_user,
  aes(
    x = targetLevel,
    y = pressRawPercent
  )
) + 
  scale_y_continuous(lim=c(0,100), breaks = seq(0, 100, by = 20) )  +
  geom_hline(yintercept=5, linetype="dashed", color = "#5D6D7E") + 
  geom_hline(yintercept=35, linetype="dashed", color = "#5D6D7E") + 
  geom_hline(yintercept=70, linetype="dashed", color = "#5D6D7E") + 
  geom_hline(yintercept=98, linetype="dashed", color = "#5D6D7E")+ 
  geom_violin(fill="#52BE80", scale = "count", width = 1.5, position=position_dodge())+ 
  geom_boxplot(width = 0.06, outliers = FALSE, fill="#E5E7E9") + 
  coord_flip()

twolovel_user_press

twolovel_user_press + theme( # remove the vertical grid lines
          panel.background = element_blank(),
          panel.grid.major.y = element_blank() ,
          # explicitly set the horizontal lines (or they will disappear too)
          panel.grid.major.x = element_line( size=.1, color="gray" ),
          axis.title.x = element_blank(),
          axis.text.x=element_blank(),
          axis.ticks.x = element_blank(),
          axis.title.y = element_blank(),
          axis.text.y=element_blank(),
          axis.ticks.y = element_blank()
    )

ggsave("2level_violin.pdf", width = 4, height = 4)


```

##### confusion table
```{r warning=FALSE}
library(cvms)
conf_mat <- confusion_matrix(targets = log_twolevel_user$targetLevel,
                             predictions = log_twolevel_user$pressedLevel)

conf_mat

twolovel_confusion <- plot_confusion_matrix(conf_mat$`Confusion Matrix`[[1]],
  add_normalized = FALSE,
  add_row_percentages = FALSE)

twolovel_confusion

twolovel_confusion + theme( # remove the vertical grid lines
          panel.background = element_blank(),
          panel.grid.major.y = element_blank() ,
          # explicitly set the horizontal lines (or they will disappear too)
          panel.grid.major.x = element_blank() ,
          axis.title.x = element_blank(),
          axis.text.x=element_blank(),
          axis.ticks.x = element_blank(),
          axis.title.y = element_blank(),
          axis.text.y=element_blank(),
          axis.ticks.y = element_blank()
    )

ggsave("2level_confusion.pdf", width = 4, height = 4)

conf_mat <- confusion_matrix(targets = log_twolevel_user$targetLevel,
                             predictions = log_twolevel_user$pressLevel_user)

conf_mat

plot_confusion_matrix(conf_mat$`Confusion Matrix`[[1]],
  add_normalized = FALSE,
  add_row_percentages = FALSE)

```

#### Each user
```{r warning=FALSE}

twolovel_each_user_press <- ggplot(log_twolevel_user,
  aes(
    x = reorder(id, desc(id)),
    y = pressRawPercent,
    color = targetLevel,
  )
) + 
  scale_y_continuous(lim=c(0,100), breaks = seq(0, 100, by = 20) )  +
  scale_colour_manual(values=level_cols)+
  geom_hline(yintercept=5, linetype="dashed", color = "#5D6D7E") + 
  geom_hline(yintercept=35, linetype="dashed", color = "#5D6D7E") + 
  geom_hline(yintercept=70, linetype="dashed", color = "#5D6D7E") + 
  geom_hline(yintercept=98, linetype="dashed", color = "#5D6D7E")+ 
  geom_boxplot(outliers = FALSE, fill=NA, position=position_identity(), alpha = 0.7, width = 0.6) + 
  coord_flip()
  

twolovel_each_user_press

twolovel_each_user_press + theme( # remove the vertical grid lines
          panel.background = element_blank(),
          panel.grid.major.y = element_blank() ,
          # explicitly set the horizontal lines (or they will disappear too)
          panel.grid.major.x = element_line( size=.1, color="gray" ),
          axis.title.x = element_blank(),
          axis.text.x=element_blank(),
          axis.ticks.x = element_blank(),
          axis.title.y = element_blank(),
          axis.text.y=element_blank(),
          axis.ticks.y = element_blank(),
          legend.position="none",
    )

ggsave("2level_user.pdf", width = 4, height = 12)

```


### Three levels
#### actual press - user threshold
```{r warning=FALSE}

log_threelevel <- trial_log_filtered %>%
  filter(levelCounts == c("3"))

log_threelevel_user <- log_threelevel %>% 
  group_by(id, targetLevel) %>% 
  mutate(
    pressRawPercent = pressedRaw * 100.0 / 255.0,
  )  %>%
  ungroup()

log_threelevel_user_dist <- log_threelevel_user %>% 
  group_by(id, targetLevel) %>% 
  summarize(
    press_ave = sum(pressRawPercent) / n(),
    n_trials = n()
  )%>%
  mutate(
    press_ave_mm = press_ave * 4.0 / 100.0,
  )  %>%
  ungroup()

log_threelevel_user_dist

log_threelevel_user_level_summary <- log_threelevel_user_dist  %>%
  group_by(targetLevel) %>%
  summarize(
    meanDist = press_ave_mm %>% mean(na.rm=TRUE),
    lowCIDist = ci(press_ave_mm)[2] %>% pmax(0),
    highCIDist = ci(press_ave_mm)[3] %>% pmin(100),
    sdDist = ci(press_ave_mm)[4],
    stdDist = sd(press_ave_mm)) %>%
  ungroup() %>%
  arrange(targetLevel)

log_threelevel_user_level_summary

log_threelevel_user_quantile <- log_threelevel_user%>%
  group_by(id, targetLevel) %>%
  summarize(
    lower_outlier = boxplot.stats(pressedRaw)$stats[c(1)],
    lower = boxplot.stats(pressedRaw)$stats[c(2)],
    median = boxplot.stats(pressedRaw)$stats[c(3)],
    upper = boxplot.stats(pressedRaw)$stats[c(4)],
    upper_outlier = boxplot.stats(pressedRaw)$stats[c(5)],
  ) %>%
  ungroup() %>%
  arrange(id, targetLevel)

library(reshape2) # for dcast

melted_threshold <- melt(log_threelevel_user_quantile, id.vars = c("id", "targetLevel"), measure.vars = c("lower_outlier", "lower", "median", "upper", "upper_outlier"))
cast_threshold <- dcast(melted_threshold, id~targetLevel * variable, value.var="value") %>% 
  group_by(id) %>%
  mutate(
    full_threshold =  median(c(full_lower_outlier, full_lower,medium_upper, medium_upper_outlier)),
    full_threshold_percent = full_threshold * 100.0 / 255.0,
    medium_threshold =  median(c(medium_lower_outlier, medium_lower,light_upper, light_upper_outlier)),
    medium_threshold_percent = medium_threshold * 100.0 / 255.0,
    
  ) %>%
  ungroup()

threelevel_threshold_summary <- cast_threshold  %>%
  summarize(
    meanFullThreshold = full_threshold_percent %>% mean(na.rm=TRUE),
    lowCIFullThreshold = ci(full_threshold_percent)[2] %>% pmax(0),
    highCIFullThreshold = ci(full_threshold_percent)[3] %>% pmin(255),
    sdFullThreshold = ci(full_threshold_percent)[4],
    stdFullThreshold = sd(full_threshold_percent),
    meanMediumThreshold = medium_threshold_percent %>% mean(na.rm=TRUE),
    lowCIMediumThreshold = ci(medium_threshold_percent)[2] %>% pmax(0),
    highCIMediumThreshold = ci(medium_threshold_percent)[3] %>% pmin(255),,
    sdMediumThreshold = ci(medium_threshold_percent)[4],
    stdMediumThreshold = sd(medium_threshold_percent))

threelevel_threshold_summary

log_threelevel_user <- merge(log_threelevel_user, cast_threshold,
                          by = 'id', all = TRUE)

log_threelevel_user <- log_threelevel_user %>% 
  mutate(
    pressLevel_user = ifelse(pressedRaw >= full_threshold, "full", ifelse(pressedRaw >= medium_threshold, "medium", "light")),
    isSuccessful_user = (targetLevel == pressLevel_user)
  )


threelovel_user_press <- ggplot(log_threelevel_user,
  aes(
    x = targetLevel,
    y = pressRawPercent
  )
) + 
  scale_y_continuous(lim=c(0,100), breaks = seq(0, 100, by = 20) )  +
  geom_hline(yintercept=5, linetype="dashed", color = "#5D6D7E") + 
  geom_hline(yintercept=35, linetype="dashed", color = "#5D6D7E") + 
  geom_hline(yintercept=70, linetype="dashed", color = "#5D6D7E") + 
  geom_hline(yintercept=98, linetype="dashed", color = "#5D6D7E")+ 
  geom_violin(fill="#52BE80", scale = "count", width = 1.5, position=position_dodge())+ 
  geom_boxplot(width = 0.06, outliers = FALSE, fill="#E5E7E9")  + 
  coord_flip()

threelovel_user_press

threelovel_user_press + theme( # remove the vertical grid lines
          panel.background = element_blank(),
          panel.grid.major.y = element_line( size=.1, color="gray" ),
          # explicitly set the horizontal lines (or they will disappear too)
          panel.grid.major.x = element_blank() ,
          axis.title.x = element_blank(),
          axis.text.x=element_blank(),
          axis.ticks.x = element_blank(),
          axis.title.y = element_blank(),
          axis.text.y=element_blank(),
          axis.ticks.y = element_blank()
    )

ggsave("3level_violin.pdf", width = 4, height = 4)

```


##### confusion table
```{r warning=FALSE}
library(cvms)
conf_mat <- confusion_matrix(targets = log_threelevel_user$targetLevel,
                             predictions = log_threelevel_user$pressedLevel)

conf_mat

threelevel_confusion <- plot_confusion_matrix(conf_mat$`Confusion Matrix`[[1]],
  add_normalized = FALSE,
  add_row_percentages = FALSE,
  class_order = c("full", "medium", "light"))

threelevel_confusion

threelevel_confusion + theme( # remove the vertical grid lines
          panel.background = element_blank(),
          panel.grid.major.y = element_blank() ,
          # explicitly set the horizontal lines (or they will disappear too)
          panel.grid.major.x = element_blank() ,
          axis.title.x = element_blank(),
          axis.text.x=element_blank(),
          axis.ticks.x = element_blank(),
          axis.title.y = element_blank(),
          axis.text.y=element_blank(),
          axis.ticks.y = element_blank()
    )

ggsave("3level_confusion.pdf", width = 4, height = 4)


conf_mat <- confusion_matrix(targets = log_threelevel_user$targetLevel,
                             predictions = log_threelevel_user$pressLevel_user)

conf_mat

plot_confusion_matrix(conf_mat$`Confusion Matrix`[[1]],
  add_normalized = FALSE,
  add_row_percentages = FALSE,
  class_order = c("full", "medium", "light"))

```


#### Each user
```{r warning=FALSE}

threelovel_each_user_press <- ggplot(log_threelevel_user,
  aes(
    x = reorder(id, desc(id)),
    y = pressRawPercent,
    color = targetLevel,
  )
) + 
  scale_y_continuous(lim=c(0,100), breaks = seq(0, 100, by = 20) )  +
  scale_colour_manual(values = level_cols) + 
  geom_hline(yintercept=5, linetype="dashed", color = "#5D6D7E") + 
  geom_hline(yintercept=35, linetype="dashed", color = "#5D6D7E") + 
  geom_hline(yintercept=70, linetype="dashed", color = "#5D6D7E") + 
  geom_hline(yintercept=98, linetype="dashed", color = "#5D6D7E")+ 
  geom_boxplot(outliers = FALSE, fill=NA, position=position_identity(), alpha = 0.7, width = 0.6) + 
  coord_flip()
  

threelovel_each_user_press

threelovel_each_user_press + theme( # remove the vertical grid lines
          panel.background = element_blank(),
          panel.grid.major.y = element_blank() ,
          # explicitly set the horizontal lines (or they will disappear too)
          panel.grid.major.x = element_line( size=.1, color="gray" ),
          axis.title.x = element_blank(),
          axis.text.x=element_blank(),
          axis.ticks.x = element_blank(),
          axis.title.y = element_blank(),
          axis.text.y=element_blank(),
          axis.ticks.y = element_blank(),
          legend.position="none",
    )

ggsave("3level_user.pdf", width = 4, height = 12)

```


### Four levels

#### actual press - user threshold
```{r warning=FALSE}
log_fourlevel <- trial_log_filtered %>%
  filter(levelCounts == c("4"))

log_fourlevel_user <- log_fourlevel %>% 
  group_by(id, targetLevel) %>% 
  mutate(
    pressRawPercent = pressedRaw * 100.0 / 255.0,
  ) %>% 
  ungroup()

log_fourlevel_user_dist <- log_fourlevel_user %>% 
  group_by(id, targetLevel) %>% 
  summarize(
    press_ave = sum(pressRawPercent) / n(),
    n_trials = n()
  )%>%
  ungroup()

log_fourlevel_user_dist

log_fourlevel_user_level_summary <- log_fourlevel_user_dist  %>%
  group_by(targetLevel) %>%
  summarize(
    meanDist = press_ave %>% mean(na.rm=TRUE),
    lowCIDist = ci(press_ave)[2] %>% pmax(0),
    highCIDist = ci(press_ave)[3] %>% pmin(100),
    sdDist = ci(press_ave)[4],
    stdDist = sd(press_ave)) %>%
  ungroup() %>%
  arrange(targetLevel)

log_fourlevel_user_level_summary

log_fourlevel_user_quantile <- log_fourlevel_user%>%
  group_by(id, targetLevel) %>%
  summarize(
    lower_outlier = boxplot.stats(pressedRaw)$stats[c(1)],
    lower = boxplot.stats(pressedRaw)$stats[c(2)],
    median = boxplot.stats(pressedRaw)$stats[c(3)],
    upper = boxplot.stats(pressedRaw)$stats[c(4)],
    upper_outlier = boxplot.stats(pressedRaw)$stats[c(5)],
  ) %>%
  ungroup() %>%
  arrange(id, targetLevel)

library(reshape2) # for dcast

melted_threshold <- melt(log_fourlevel_user_quantile, id.vars = c("id", "targetLevel"), measure.vars = c("lower_outlier", "lower", "median", "upper", "upper_outlier"))
cast_threshold <- dcast(melted_threshold, id~targetLevel * variable, value.var="value") %>% 
  group_by(id) %>%
  mutate(
    full_threshold =  median(c(full_lower_outlier, full_lower,mediumHigh_upper, mediumHigh_upper_outlier)),
    full_threshold_percent = full_threshold * 100.0 / 255.0,
    mediumHigh_threshold =  median(c(mediumHigh_lower_outlier, mediumHigh_lower,mediumLow_upper, mediumLow_upper_outlier)),
    mediumHigh_threshold_percent = mediumHigh_threshold * 100.0 / 255.0,
    mediumLow_threshold =  median(c(mediumLow_lower_outlier, mediumLow_lower,light_upper, light_upper_outlier)),
    mediumLow_threshold_percent = mediumLow_threshold * 100.0 / 255.0,
  ) %>%
  ungroup()

fourlevel_threshold_summary <- cast_threshold  %>%
  summarize(
    meanFullThreshold = full_threshold_percent %>% mean(na.rm=TRUE),
    lowCIFullThreshold = ci(full_threshold_percent)[2] %>% pmax(0),
    highCIFullThreshold = ci(full_threshold_percent)[3] %>% pmin(255),
    sdFullThreshold = ci(full_threshold_percent)[4],
    stdFullThreshold = sd(full_threshold_percent),
    meanMediumHighThreshold = mediumHigh_threshold_percent %>% mean(na.rm=TRUE),
    lowCIMediumHighThreshold = ci(mediumHigh_threshold_percent)[2] %>% pmax(0),
    highCIMediumHighThreshold = ci(mediumHigh_threshold_percent)[3] %>% pmin(255),
    sdMediumHighThreshold = ci(mediumHigh_threshold_percent)[4],
    stdMediumHighThreshold = sd(mediumHigh_threshold_percent),
    meanMediumLowThreshold = mediumLow_threshold_percent %>% mean(na.rm=TRUE),
    lowCIMediumLowThreshold = ci(mediumLow_threshold_percent)[2] %>% pmax(0),
    highCIMediumLowThreshold = ci(mediumLow_threshold_percent)[3] %>% pmin(255),
    sdMediumLowThreshold = ci(mediumLow_threshold_percent)[4],
    stdMediumLowThreshold = sd(mediumLow_threshold_percent))

fourlevel_threshold_summary

log_fourlevel_user <- merge(log_fourlevel_user, cast_threshold,
                          by = 'id', all = TRUE)

log_fourlevel_user <- log_fourlevel_user %>% 
  mutate(
    pressLevel_user = ifelse(pressedRaw >= full_threshold, "full", ifelse(pressedRaw >= mediumHigh_threshold, "mediumHigh", ifelse(pressedRaw >= mediumLow_threshold, "mediumLow", "light"))),
    isSuccessful_user = (targetLevel == pressLevel_user)
  )


fourlovel_user_press <- ggplot(log_fourlevel_user,
  aes(
    x = targetLevel,
    y = pressRawPercent
  )
) + 
  scale_y_continuous(lim=c(0,100), breaks = seq(0, 100, by = 20) )  +
  geom_hline(yintercept=5, linetype="dashed", color = "#5D6D7E") + 
  geom_hline(yintercept=35, linetype="dashed", color = "#5D6D7E") + 
  geom_hline(yintercept=70, linetype="dashed", color = "#5D6D7E") + 
  geom_hline(yintercept=98, linetype="dashed", color = "#5D6D7E")+ 
  geom_violin(fill="#52BE80", scale = "count", width = 1.5, position=position_dodge())+ 
  geom_boxplot(width = 0.06, outliers = FALSE, fill="#E5E7E9")   + 
  coord_flip()


fourlovel_user_press

fourlovel_user_press + theme( # remove the vertical grid lines
          panel.background = element_blank(),
          panel.grid.major.y = element_line( size=.1, color="gray" ),
          # explicitly set the horizontal lines (or they will disappear too)
          panel.grid.major.x = element_blank() ,
          axis.title.x = element_blank(),
          axis.text.x=element_blank(),
          axis.ticks.x = element_blank(),
          axis.title.y = element_blank(),
          axis.text.y=element_blank(),
          axis.ticks.y = element_blank()
    )

ggsave("4level_violin.pdf", width = 4, height = 4)

```


##### confusion table
```{r warning=FALSE}
library(cvms)
conf_mat <- confusion_matrix(targets = log_fourlevel_user$targetLevel,
                             predictions = log_fourlevel_user$pressedLevel)

conf_mat

fourlevel_confusion <- plot_confusion_matrix(conf_mat$`Confusion Matrix`[[1]],
  add_normalized = FALSE,
  add_row_percentages = FALSE,
  class_order = c("full", "mediumHigh", "mediumLow", "light"))

fourlevel_confusion

fourlevel_confusion + theme( # remove the vertical grid lines
          panel.background = element_blank(),
          panel.grid.major.y = element_blank() ,
          # explicitly set the horizontal lines (or they will disappear too)
          panel.grid.major.x = element_blank() ,
          axis.title.x = element_blank(),
          axis.text.x=element_blank(),
          axis.ticks.x = element_blank(),
          axis.title.y = element_blank(),
          axis.text.y=element_blank(),
          axis.ticks.y = element_blank()
    )

ggsave("4level_confusion.pdf", width = 4, height = 4)

conf_mat <- confusion_matrix(targets = log_fourlevel_user$targetLevel,
                             predictions = log_fourlevel_user$pressLevel_user)

conf_mat

plot_confusion_matrix(conf_mat$`Confusion Matrix`[[1]],
  add_normalized = FALSE,
  add_row_percentages = FALSE,
  class_order = c("full", "mediumHigh", "mediumLow", "light"))


```

#### Each user
```{r warning=FALSE}


fourlovel_each_user_press <- ggplot(log_fourlevel_user,
  aes(
    x = reorder(id, desc(id)),
    y = pressRawPercent,
    color = targetLevel,
  )
) + 
  scale_y_continuous(lim=c(0,100), breaks = seq(0, 100, by = 20) )  +
  scale_colour_manual(values = level_cols) + 
  geom_hline(yintercept=5, linetype="dashed", color = "#5D6D7E") + 
  geom_hline(yintercept=35, linetype="dashed", color = "#5D6D7E") + 
  geom_hline(yintercept=70, linetype="dashed", color = "#5D6D7E") + 
  geom_hline(yintercept=98, linetype="dashed", color = "#5D6D7E")+ 
  geom_boxplot(outliers = FALSE, fill=NA, position=position_identity(), alpha = 0.7, width = 0.6) + 
  coord_flip()
  

fourlovel_each_user_press

fourlovel_each_user_press + theme( # remove the vertical grid lines
          panel.background = element_blank(),
          panel.grid.major.y = element_blank() ,
          # explicitly set the horizontal lines (or they will disappear too)
          panel.grid.major.x = element_line( size=.1, color="gray" ),
          axis.title.x = element_blank(),
          axis.text.x=element_blank(),
          axis.ticks.x = element_blank(),
          axis.title.y = element_blank(),
          axis.text.y=element_blank(),
          axis.ticks.y = element_blank(),
          legend.position="none",
    )

ggsave("4level_user.pdf", width = 4, height = 12)

```



### Accuracy levelcount - user
```{r warning=FALSE}

log_fourlevel_user_accuracy <- log_fourlevel_user %>%
  dplyr::select(id:isSuccessful, pressLevel_user, isSuccessful_user)

log_threelevel_user_accuracy <- log_threelevel_user %>%
  dplyr::select(id:isSuccessful, pressLevel_user, isSuccessful_user)

log_twolevel_user_accuracy <- log_twolevel_user %>%
  dplyr::select(id:isSuccessful, pressLevel_user, isSuccessful_user)

log_user = bind_rows(log_twolevel_user_accuracy,log_threelevel_user_accuracy, log_fourlevel_user_accuracy)

log_defult_accuracy <- log_user %>%
  group_by(id, levelCounts) %>%
  summarize(
    accuracy_ave = sum(isSuccessful) / n(),
    n_trials = n()
  ) %>%
  mutate(
    method = "default"
  ) %>%
  ungroup() %>%
  arrange(id, levelCounts)
  
log_user_accuracy <- log_user %>%
  group_by(id, levelCounts) %>%
  summarize(
    accuracy_ave = sum(isSuccessful_user) / n(),
    n_trials = n()
  ) %>%
  mutate(
    method = "user"
  ) %>%
  ungroup() %>%
  arrange(id, levelCounts)
  
log_accuracy = bind_rows(log_defult_accuracy, log_user_accuracy)


log_accuracy_summary <- log_accuracy  %>%
  group_by(levelCounts, method) %>%
  summarize(
    meanAccuracy = accuracy_ave %>% mean(na.rm=TRUE),
    lowCIAccuracy = ci(accuracy_ave)[2] %>% pmax(0),
    highCIAccuracy = ci(accuracy_ave)[3] %>% pmin(1),
    sdAccuracy = ci(accuracy_ave)[4],
    stdAccuracy = sd(accuracy_ave)) %>%
  ungroup() %>%
  arrange(method, levelCounts)

log_accuracy_summary

pd <- position_dodge(width = 0.3)
log_accuracy_summary %>% ggplot(
  aes(
    x = levelCounts,
    y = meanAccuracy,
    ymin = lowCIAccuracy,
    ymax = highCIAccuracy,
    color = method
  )
) +
  geom_pointrange(position = pd) 
```