---
title: "exp preference"
author: "Allen Yeh"
output:
  html_document: default
  pdf_document: default
---

```
```

```{r warning=FALSE}
library(tidyverse)
library(gmodels)
library(rstatix)
library(ggplot2)
library(ez)
library(ARTool)
library(emmeans)
```
### functions

```{r warning=FALSE}
percent <- function(num, digits = 2, ...) {      
  percentage <-formatC(num * 100, format = "f", digits = digits, ...)
  
  # appending "%" symbol at the end of
  # calculate percentage value
  paste0(percentage, "%")
}

INT <- function(x){
    qnorm((rank(x) - 0.5)/length(x))
}
```

### Import data

#### Read the csv file and claim the data type
```{r}

key_code = c("A", "S", "D", "F", "J", "K", "L", "Semicolon")

two_level_code = c("full", "light")
three_level_code = c("full", "medium", "light")
four_level_code = c("full", "mediumHigh", "mediumLow", "light")

level2_data <- read_csv("./../results/rating/2_levels.csv", col_types = cols(
  ID = col_integer(), 
  Mental_Demand = col_integer(),
  Physical_Demand = col_integer(),
  Temporal_Demand = col_integer(), 
  Performance = col_integer(), 
  Effort = col_integer(), 
  Frustration = col_integer(), 
  Learnability = col_integer(), 
  Light_easiness = col_integer(), 
  Full_easiness = col_integer(), 
  A_easiness = col_integer(), 
  S_easiness = col_integer(), 
  D_easiness = col_integer(), 
  F_easiness = col_integer(), 
  J_easiness = col_integer(),
  K_easiness = col_integer(), 
  L_easiness = col_integer(),
  Semicolon_easiness = col_integer()
  ))%>%
  mutate(
    levelCount = "2",
    )

level3_data <- read_csv("./../results/rating/3_levels.csv", col_types = cols(
  ID = col_integer(), 
  Mental_Demand = col_integer(),
  Physical_Demand = col_integer(),
  Temporal_Demand = col_integer(), 
  Performance = col_integer(), 
  Effort = col_integer(), 
  Frustration = col_integer(), 
  Learnability = col_integer(), 
  Light_easiness = col_integer(), 
  Medium_easiness = col_integer(), 
  Full_easiness = col_integer(), 
  A_easiness = col_integer(), 
  S_easiness = col_integer(), 
  D_easiness = col_integer(), 
  F_easiness = col_integer(), 
  J_easiness = col_integer(),
  K_easiness = col_integer(), 
  L_easiness = col_integer(),
  Semicolon_easiness = col_integer()
  ))%>%
  mutate(
    levelCount = "3",
    )

level4_data <- read_csv("./../results/rating/4_levels.csv", col_types = cols(
  ID = col_integer(), 
  Mental_Demand = col_integer(),
  Physical_Demand = col_integer(),
  Temporal_Demand = col_integer(), 
  Performance = col_integer(), 
  Effort = col_integer(), 
  Frustration = col_integer(), 
  Learnability = col_integer(), 
  Light_easiness = col_integer(), 
  MediumLow_easiness = col_integer(),
  MediumHigh_easiness = col_integer(),
  Full_easiness = col_integer(), 
  A_easiness = col_integer(), 
  S_easiness = col_integer(), 
  D_easiness = col_integer(), 
  F_easiness = col_integer(), 
  J_easiness = col_integer(),
  K_easiness = col_integer(), 
  L_easiness = col_integer(),
  Semicolon_easiness = col_integer()
  ))%>%
  mutate(
    levelCount = "4",
    )


level2_data_tlx <- level2_data %>%
  dplyr::select(ID:Learnability, levelCount)

level2_data_tlx_long <- level2_data_tlx %>%
  pivot_longer(
    cols = Mental_Demand:Learnability, # Selects columns that start with "Test"
    names_to = "Category",     # Name for the new column holding the original column names (e.g., Test1)
    values_to = "Score"        # Name for the new column holding the values (e.g., 85, 92)
  )

level3_data_tlx <- level3_data %>%
  dplyr::select(ID:Learnability, levelCount)

level3_data_tlx_long <- level3_data_tlx %>%
  pivot_longer(
    cols = Mental_Demand:Learnability, # Selects columns that start with "Test"
    names_to = "Category",     # Name for the new column holding the original column names (e.g., Test1)
    values_to = "Score"        # Name for the new column holding the values (e.g., 85, 92)
  )

level4_data_tlx <- level4_data %>%
  dplyr::select(ID:Learnability, levelCount)

level4_data_tlx_long <- level4_data_tlx %>%
  pivot_longer(
    cols = Mental_Demand:Learnability, # Selects columns that start with "Test"
    names_to = "Category",     # Name for the new column holding the original column names (e.g., Test1)
    values_to = "Score"        # Name for the new column holding the values (e.g., 85, 92)
  )

log_tlx_ratings = bind_rows(level2_data_tlx_long, level3_data_tlx_long, level4_data_tlx_long)

count_level <- c("2", "3", "4")

```


#### Mental Demand
```{r warning=FALSE}

log_MD <- log_tlx_ratings %>%
  filter(Category == "Mental_Demand")

log_MD$ID = factor(log_MD$ID)
log_MD$levelCount = factor(log_MD$levelCount)

boxplot(Score~levelCount,data=log_MD, main="Mental Demand",
   xlab="likert scale", ylab="level counts", horizontal=TRUE, outline = FALSE)


MD_summary <- log_MD %>%
  group_by(levelCount) %>%
  summarize(
    meanScore = Score %>% mean(na.rm=TRUE),
    lowCI = ci(Score)[2]%>% pmax(0),
    highCI = ci(Score)[3]%>% pmin(7),
    sd = ci(Score)[4],
    std = Score %>% sd())

MD_summary

# line + dot
MD_graph <- ggplot(MD_summary) +
  geom_pointrange( aes(x=reorder(levelCount, desc(levelCount)), y=meanScore, ymin=lowCI, ymax=highCI), colour="#d68910", alpha=0.9, size=0.8) +
  scale_y_continuous(lim=c(1,7)) + 
  coord_flip()

MD_graph

MD_graph + theme( # remove the vertical grid lines
          panel.background = element_blank(),
          panel.grid.major.y = element_blank() ,
          # explicitly set the horizontal lines (or they will disappear too)
          panel.grid.major.x = element_line( size=.1, color="gray" ),
          axis.title.x = element_blank(),
          axis.text.x=element_blank(),
          axis.ticks.x = element_blank(),
          axis.title.y = element_blank(),
          axis.text.y=element_blank(),
          axis.ticks.y = element_blank()
    )

ggsave("mental_demand_levels.pdf", width = 3, height = 3)
```
#### analysis

```{r warning=FALSE}


m = aov(Score ~ levelCount, data=log_MD) # make anova-type linear model
shapiro.test(residuals(m))
qqnorm(residuals(m)); qqline(residuals(m)) # Q-Q plot

# df has subjects (S), one within-Ss factor (X) w/levels (a,b,c), and continuous response (Y)
library(coin)
log_MD$ID = factor(log_MD$ID)
friedman_test(Score ~ levelCount | ID, data=log_MD, distribution="asymptotic")
friedman_effsize(Score ~ levelCount | ID, data=log_MD)

# 
# library(reshape2) # for dcast
# df2 <- dcast(log_MD, ID ~ levelCount, value.var="Score") # make wide-format table
# ab = wilcox.test(df2$"2", df2$"3", paired=TRUE) # a vs. b
# ac = wilcox.test(df2$"2", df2$"4", paired=TRUE) # a vs. c
# bc = wilcox.test(df2$"3", df2$"4", paired=TRUE) # b vs. c
# p.adjust(c(ab$p.value, ac$p.value, bc$p.value), method="holm")

pairwise.wilcox.test(x = log_MD$Score,
                     g = log_MD$levelCount,
                     p.adjust.method = "holm",
                     paired = TRUE)
```

Main effect on levelCounts: 2 is less mental demand than 3 and 4, 3 is less mental demand than 4

#### Physical demand
```{r warning=FALSE}
log_PD <- log_tlx_ratings %>%
  filter(Category == "Physical_Demand")

log_PD$ID = factor(log_PD$ID)
log_PD$levelCount = factor(log_PD$levelCount)

boxplot(Score~levelCount,data=log_PD, main="Mental Demand",
   xlab="likert scale", ylab="level counts", horizontal=TRUE, outline = FALSE)


PD_summary <- log_PD %>%
  group_by(levelCount) %>%
  summarize(
    meanScore = Score %>% mean(na.rm=TRUE),
    lowCI = ci(Score)[2]%>% pmax(0),
    highCI = ci(Score)[3]%>% pmin(7),
    sd = ci(Score)[4],
    std = Score %>% sd())

PD_summary

# line + dot
PD_graph <- ggplot(PD_summary) +
  geom_pointrange( aes(x=reorder(levelCount, desc(levelCount)), y=meanScore, ymin=lowCI, ymax=highCI), colour="#2e4053", alpha=0.9, size=0.8) +
  scale_y_continuous(lim=c(1,7)) + 
  coord_flip()

PD_graph

PD_graph + theme( # remove the vertical grid lines
          panel.background = element_blank(),
          panel.grid.major.y = element_blank() ,
          # explicitly set the horizontal lines (or they will disappear too)
          panel.grid.major.x = element_line( size=.1, color="gray" ),
          axis.title.x = element_blank(),
          axis.text.x=element_blank(),
          axis.ticks.x = element_blank(),
          axis.title.y = element_blank(),
          axis.text.y=element_blank(),
          axis.ticks.y = element_blank()
    )

ggsave("physical_demand_levels.pdf", width = 3, height = 3)
```
#### analysis

```{r warning=FALSE}
m = aov(Score ~ levelCount, data=log_PD) # make anova-type linear model
shapiro.test(residuals(m))
qqnorm(residuals(m)); qqline(residuals(m)) # Q-Q plot

# df has subjects (S), one within-Ss factor (X) w/levels (a,b,c), and continuous response (Y)
library(coin)
log_PD$ID = factor(log_PD$ID)
friedman_test(Score ~ levelCount | ID, data=log_PD, distribution="asymptotic")

friedman_effsize(Score ~ levelCount | ID, data=log_PD)

# library(reshape2) # for dcast
# df2 <- dcast(log_PD, ID ~ levelCount, value.var="Score") # make wide-format table
# ab = wilcox.test(df2$"2", df2$"3", paired=TRUE) # a vs. b
# ac = wilcox.test(df2$"2", df2$"4", paired=TRUE) # a vs. c
# bc = wilcox.test(df2$"3", df2$"4", paired=TRUE) # b vs. c
# p.adjust(c(ab$p.value, ac$p.value, bc$p.value), method="holm")

pairwise.wilcox.test(x = log_PD$Score,
                     g = log_PD$levelCount,
                     p.adjust.method = "holm",
                     paired = TRUE)
```

Main effect on levelCounts: 2 is less physical demand than 3 and 4, 3 is less physical demand than 4


#### Temporal demand
```{r warning=FALSE}

log_TD <- log_tlx_ratings %>%
  filter(Category == "Temporal_Demand")

log_TD$ID = factor(log_TD$ID)
log_TD$levelCount = factor(log_TD$levelCount)

boxplot(Score~levelCount,data=log_TD, main="Mental Demand",
   xlab="likert scale", ylab="level counts", horizontal=TRUE, outline = FALSE)


TD_summary <- log_TD %>%
  group_by(levelCount) %>%
  summarize(
    meanScore = Score %>% mean(na.rm=TRUE),
    lowCI = ci(Score)[2]%>% pmax(0),
    highCI = ci(Score)[3]%>% pmin(7),
    sd = ci(Score)[4],
    std = Score %>% sd())

TD_summary

# line + dot
TD_graph <- ggplot(TD_summary) +
  geom_pointrange( aes(x=reorder(levelCount, desc(levelCount)), y=meanScore, ymin=lowCI, ymax=highCI), colour="#884ea0", alpha=0.9, size=0.8) +
  scale_y_continuous(lim=c(1,7)) + 
  coord_flip()

TD_graph

TD_graph + theme( # remove the vertical grid lines
          panel.background = element_blank(),
          panel.grid.major.y = element_blank() ,
          # explicitly set the horizontal lines (or they will disappear too)
          panel.grid.major.x = element_line( size=.1, color="gray" ),
          axis.title.x = element_blank(),
          axis.text.x=element_blank(),
          axis.ticks.x = element_blank(),
          axis.title.y = element_blank(),
          axis.text.y=element_blank(),
          axis.ticks.y = element_blank()
    )

ggsave("temporal_demand_levels.pdf", width = 3, height = 3)

```
#### analysis

```{r warning=FALSE}
m = aov(Score ~ levelCount, data=log_TD) # make anova-type linear model
shapiro.test(residuals(m))
qqnorm(residuals(m)); qqline(residuals(m)) # Q-Q plot

# df has subjects (S), one within-Ss factor (X) w/levels (a,b,c), and continuous response (Y)
library(coin)
log_TD$ID = factor(log_TD$ID)
friedman_test(Score ~ levelCount | ID, data=log_TD, distribution="asymptotic")
friedman_effsize(Score ~ levelCount | ID, data=log_TD)

# library(reshape2) # for dcast
# df2 <- dcast(log_TD, ID ~ levelCount, value.var="Score") # make wide-format table
# ab = wilcox.test(df2$"2", df2$"3", paired=TRUE) # a vs. b
# ac = wilcox.test(df2$"2", df2$"4", paired=TRUE) # a vs. c
# bc = wilcox.test(df2$"3", df2$"4", paired=TRUE) # b vs. c
# p.adjust(c(ab$p.value, ac$p.value, bc$p.value), method="holm")

pairwise.wilcox.test(x = log_PD$Score,
                     g = log_PD$levelCount,
                     p.adjust.method = "holm",
                     paired = TRUE)

```

Main effect on levelCounts: 2 is less temporal demand than 3 and 4, 3 is less temporal demand than 4


#### Performance
```{r warning=FALSE}

log_P <- log_tlx_ratings %>%
  filter(Category == "Performance")

log_P$ID = factor(log_P$ID)
log_P$levelCount = factor(log_P$levelCount)

boxplot(Score~levelCount,data=log_P, main="Mental Demand",
   xlab="likert scale", ylab="level counts", horizontal=TRUE, outline = FALSE)


P_summary <- log_P %>%
  group_by(levelCount) %>%
  summarize(
    meanScore = Score %>% mean(na.rm=TRUE),
    lowCI = ci(Score)[2]%>% pmax(0),
    highCI = ci(Score)[3]%>% pmin(7),
    sd = ci(Score)[4],
    std = Score %>% sd())

P_summary

# line + dot
P_graph <- ggplot(P_summary) +
  geom_pointrange( aes(x=reorder(levelCount, desc(levelCount)), y=meanScore, ymin=lowCI, ymax=highCI), colour="#138d75", alpha=0.9, size=0.8) +
  scale_y_reverse(lim=c(7,1)) + 
  coord_flip()

P_graph

P_graph + theme( # remove the vertical grid lines
          panel.background = element_blank(),
          panel.grid.major.y = element_blank() ,
          # explicitly set the horizontal lines (or they will disappear too)
          panel.grid.major.x = element_line( size=.1, color="gray" ),
          axis.title.x = element_blank(),
          axis.text.x=element_blank(),
          axis.ticks.x = element_blank(),
          axis.title.y = element_blank(),
          axis.text.y=element_blank(),
          axis.ticks.y = element_blank()
    )

ggsave("performance_levels.pdf", width = 3, height = 3)


```
#### analysis

```{r warning=FALSE}
m = aov(Score ~ levelCount, data=log_P) # make anova-type linear model
shapiro.test(residuals(m))
qqnorm(residuals(m)); qqline(residuals(m)) # Q-Q plot

# df has subjects (S), one within-Ss factor (X) w/levels (a,b,c), and continuous response (Y)
library(coin)
log_P$ID = factor(log_P$ID)
friedman_test(Score ~ levelCount | ID, data=log_P, distribution="asymptotic")
friedman_effsize(Score ~ levelCount | ID, data=log_P)

# library(reshape2) # for dcast
# df2 <- dcast(log_P, ID ~ levelCount, value.var="Score") # make wide-format table
# ab = wilcox.test(df2$"2", df2$"3", paired=TRUE) # a vs. b
# ac = wilcox.test(df2$"2", df2$"4", paired=TRUE) # a vs. c
# bc = wilcox.test(df2$"3", df2$"4", paired=TRUE) # b vs. c
# p.adjust(c(ab$p.value, ac$p.value, bc$p.value), method="holm")

pairwise.wilcox.test(x = log_P$Score,
                     g = log_P$levelCount,
                     p.adjust.method = "holm",
                     paired = TRUE)

```

Main effect on levelCounts: 2 is better than 3 and 4, 3 is better than 4

#### Effort
```{r warning=FALSE}


log_E <- log_tlx_ratings %>%
  filter(Category == "Effort")

log_E$ID = factor(log_E$ID)
log_E$levelCount = factor(log_E$levelCount)

boxplot(Score~levelCount,data=log_E, main="Mental Demand",
   xlab="likert scale", ylab="level counts", horizontal=TRUE, outline = FALSE)


E_summary <- log_E %>%
  group_by(levelCount) %>%
  summarize(
    meanScore = Score %>% mean(na.rm=TRUE),
    lowCI = ci(Score)[2]%>% pmax(0),
    highCI = ci(Score)[3]%>% pmin(7),
    sd = ci(Score)[4],
    std = Score %>% sd())

E_summary

# line + dot
E_graph <- ggplot(E_summary) +
  geom_pointrange( aes(x=reorder(levelCount, desc(levelCount)), y=meanScore, ymin=lowCI, ymax=highCI), colour="#273746", alpha=0.9, size=0.8) +
  scale_y_continuous(lim=c(1,7)) + 
  coord_flip()

E_graph

E_graph + theme( # remove the vertical grid lines
          panel.background = element_blank(),
          panel.grid.major.y = element_blank() ,
          # explicitly set the horizontal lines (or they will disappear too)
          panel.grid.major.x = element_line( size=.1, color="gray" ),
          axis.title.x = element_blank(),
          axis.text.x=element_blank(),
          axis.ticks.x = element_blank(),
          axis.title.y = element_blank(),
          axis.text.y=element_blank(),
          axis.ticks.y = element_blank()
    )

ggsave("effort_levels.pdf", width = 3, height = 3)


```
#### analysis

```{r warning=FALSE}

m = aov(Score ~ levelCount, data=log_E) # make anova-type linear model
shapiro.test(residuals(m))
qqnorm(residuals(m)); qqline(residuals(m)) # Q-Q plot

# df has subjects (S), one within-Ss factor (X) w/levels (a,b,c), and continuous response (Y)
library(coin)
log_E$ID = factor(log_E$ID)
friedman_test(Score ~ levelCount | ID, data=log_E, distribution="asymptotic")
friedman_effsize(Score ~ levelCount | ID, data=log_E)


# library(reshape2) # for dcast
# df2 <- dcast(log_E, ID ~ levelCount, value.var="Score") # make wide-format table
# ab = wilcox.test(df2$"2", df2$"3", paired=TRUE) # a vs. b
# ac = wilcox.test(df2$"2", df2$"4", paired=TRUE) # a vs. c
# bc = wilcox.test(df2$"3", df2$"4", paired=TRUE) # b vs. c
# p.adjust(c(ab$p.value, ac$p.value, bc$p.value), method="holm")

pairwise.wilcox.test(x = log_E$Score,
                     g = log_E$levelCount,
                     p.adjust.method = "holm",
                     paired = TRUE)

```

Main effect on levelCounts: 2 is less effort than 3 and 4, 3 is less effort than 4


#### Frustration
```{r warning=FALSE}


log_F <- log_tlx_ratings %>%
  filter(Category == "Frustration")

log_F$ID = factor(log_F$ID)
log_F$levelCount = factor(log_F$levelCount)

boxplot(Score~levelCount,data=log_F, main="Mental Demand",
   xlab="likert scale", ylab="level counts", horizontal=TRUE, outline = FALSE)


F_summary <- log_F %>%
  group_by(levelCount) %>%
  summarize(
    meanScore = Score %>% mean(na.rm=TRUE),
    lowCI = ci(Score)[2]%>% pmax(0),
    highCI = ci(Score)[3]%>% pmin(7),
    sd = ci(Score)[4],
    std = Score %>% sd())

F_summary

# line + dot
F_graph <- ggplot(F_summary) +
  geom_pointrange( aes(x=reorder(levelCount, desc(levelCount)), y=meanScore, ymin=lowCI, ymax=highCI), colour="#cb4335", alpha=0.9, size=0.8) +
  scale_y_continuous(lim=c(1,7)) + 
  coord_flip()

F_graph

F_graph + theme( # remove the vertical grid lines
          panel.background = element_blank(),
          panel.grid.major.y = element_blank() ,
          # explicitly set the horizontal lines (or they will disappear too)
          panel.grid.major.x = element_line( size=.1, color="gray" ),
          axis.title.x = element_blank(),
          axis.text.x=element_blank(),
          axis.ticks.x = element_blank(),
          axis.title.y = element_blank(),
          axis.text.y=element_blank(),
          axis.ticks.y = element_blank()
    )

ggsave("frustration_levels.pdf", width = 3, height = 3)

```
#### analysis

```{r warning=FALSE}
m = aov(Score ~ levelCount, data=log_F) # make anova-type linear model
shapiro.test(residuals(m))
qqnorm(residuals(m)); qqline(residuals(m)) # Q-Q plot

# df has subjects (S), one within-Ss factor (X) w/levels (a,b,c), and continuous response (Y)
library(coin)
log_F$ID = factor(log_F$ID)
friedman_test(Score ~ levelCount | ID, data=log_F, distribution="asymptotic")
friedman_effsize(Score ~ levelCount | ID, data=log_F)

# library(reshape2) # for dcast
# df2 <- dcast(log_F, ID ~ levelCount, value.var="Score") # make wide-format table
# ab = wilcox.test(df2$"2", df2$"3", paired=TRUE) # a vs. b
# ac = wilcox.test(df2$"2", df2$"4", paired=TRUE) # a vs. c
# bc = wilcox.test(df2$"3", df2$"4", paired=TRUE) # b vs. c
# p.adjust(c(ab$p.value, ac$p.value, bc$p.value), method="holm")

pairwise.wilcox.test(x = log_F$Score,
                     g = log_F$levelCount,
                     p.adjust.method = "holm",
                     paired = TRUE)

```

Main effect on levelCounts: 2 is less frustration than 3 and 4


#### Learnability
```{r warning=FALSE}



log_L <- log_tlx_ratings %>%
  filter(Category == "Learnability")

log_L$ID = factor(log_L$ID)
log_L$levelCount = factor(log_L$levelCount)

boxplot(Score~levelCount,data=log_L, main="Mental Demand",
   xlab="likert scale", ylab="level counts", horizontal=TRUE, outline = FALSE)


L_summary <- log_L %>%
  group_by(levelCount) %>%
  summarize(
    meanScore = Score %>% mean(na.rm=TRUE),
    lowCI = ci(Score)[2]%>% pmax(0),
    highCI = ci(Score)[3]%>% pmin(7),
    sd = ci(Score)[4],
    std = Score %>% sd())

L_summary

# line + dot
L_graph <- ggplot(L_summary) +
  geom_pointrange( aes(x=reorder(levelCount, desc(levelCount)), y=meanScore, ymin=lowCI, ymax=highCI), colour="#2e86c1", alpha=0.9, size=0.8) +
  scale_y_reverse(lim=c(7,1)) + 
  coord_flip()

L_graph

L_graph + theme( # remove the vertical grid lines
          panel.background = element_blank(),
          panel.grid.major.y = element_blank() ,
          # explicitly set the horizontal lines (or they will disappear too)
          panel.grid.major.x = element_line( size=.1, color="gray" ),
          axis.title.x = element_blank(),
          axis.text.x=element_blank(),
          axis.ticks.x = element_blank(),
          axis.title.y = element_blank(),
          axis.text.y=element_blank(),
          axis.ticks.y = element_blank()
    )

ggsave("learnability_levels.pdf", width = 3, height = 3)


```
#### analysis

```{r warning=FALSE}
m = aov(Score ~ levelCount, data=log_L) # make anova-type linear model
shapiro.test(residuals(m))
qqnorm(residuals(m)); qqline(residuals(m)) # Q-Q plot

# df has subjects (S), one within-Ss factor (X) w/levels (a,b,c), and continuous response (Y)
library(coin)
log_L$ID = factor(log_L$ID)
friedman_test(Score ~ levelCount | ID, data=log_L, distribution="asymptotic")
friedman_effsize(Score ~ levelCount | ID, data=log_F)
# 
# library(reshape2) # for dcast
# df2 <- dcast(log_L, ID ~ levelCount, value.var="Score") # make wide-format table
# ab = wilcox.test(df2$"2", df2$"3", paired=TRUE) # a vs. b
# ac = wilcox.test(df2$"2", df2$"4", paired=TRUE) # a vs. c
# bc = wilcox.test(df2$"3", df2$"4", paired=TRUE) # b vs. c
# p.adjust(c(ab$p.value, ac$p.value, bc$p.value), method="holm")

pairwise.wilcox.test(x = log_L$Score, 
                     g = log_L$levelCount, 
                     p.adjust.method = "holm", 
                     paired = TRUE)


```

Main effect on levelCounts: 2 is easier to learn than 3 and 4, 3 is easier to learn than 4


#### 2 level - easiness
```{r warning=FALSE}

level2_data_level <- level2_data %>%
  dplyr::select(ID, Light_easiness:Full_easiness)

colnames(level2_data_level) <- c("ID", "light", "full")

level2_data_level_long <- level2_data_level %>%
  pivot_longer(
    cols = light:full, # Selects columns that start with "Test"
    names_to = "Level",     # Name for the new column holding the original column names (e.g., Test1)
    values_to = "Score"        # Name for the new column holding the values (e.g., 85, 92)
  )

level2_data_key <- level2_data %>%
  dplyr::select(ID, A_easiness:Semicolon_easiness)

colnames(level2_data_key) <- c("ID", "A", "S", "D", "F", "J", "K", "L", "Semicolon")

level2_data_key_long <- level2_data_key %>%
  pivot_longer(
    cols = A:Semicolon, # Selects columns that start with "Test"
    names_to = "Key",     # Name for the new column holding the original column names (e.g., Test1)
    values_to = "Score"        # Name for the new column holding the values (e.g., 85, 92)
  )

level2_data_level_long$ID = factor(level2_data_level_long$ID)
level2_data_level_long$Level = factor(level2_data_level_long$Level, two_level_code)

boxplot(Score~Level,data=level2_data_level_long, main="level easiness",
   xlab="likert scale", ylab="level", horizontal=TRUE, outline = FALSE)


level2_data_level_summary <- level2_data_level_long %>%
  group_by(Level) %>%
  summarize(
    meanScore = Score %>% mean(na.rm=TRUE),
    lowCI = ci(Score)[2]%>% pmax(0),
    highCI = ci(Score)[3]%>% pmin(7),
    sd = ci(Score)[4],
    std = Score %>% sd())

level2_data_level_summary

# line + dot
level2_data_level_graph <- ggplot(level2_data_level_summary) +
  geom_pointrange( aes(x=reorder(Level, desc(Level)), y=meanScore, ymin=lowCI, ymax=highCI), colour="#2e86c1", alpha=0.9, size=0.8) +
  scale_y_reverse(lim=c(7,1)) + 
  coord_flip()

level2_data_level_graph

level2_data_level_graph + theme( # remove the vertical grid lines
          panel.background = element_blank(),
          panel.grid.major.y = element_blank() ,
          # explicitly set the horizontal lines (or they will disappear too)
          panel.grid.major.x = element_line( size=.1, color="gray" ),
          axis.title.x = element_blank(),
          axis.text.x=element_blank(),
          axis.ticks.x = element_blank(),
          axis.title.y = element_blank(),
          axis.text.y=element_blank(),
          axis.ticks.y = element_blank()
    )

ggsave("2level_easiness_level.pdf", width = 3, height = 2)


level2_data_key_long$ID = factor(level2_data_key_long$ID)
level2_data_key_long$Key = factor(level2_data_key_long$Key, key_code)

boxplot(Score~Key,data=level2_data_key_long, main="level easiness",
   xlab="likert scale", ylab="key", horizontal=TRUE, outline = FALSE)


level2_data_key_summary <- level2_data_key_long %>%
  group_by(Key) %>%
  summarize(
    meanScore = Score %>% mean(na.rm=TRUE),
    lowCI = ci(Score)[2]%>% pmax(0),
    highCI = ci(Score)[3]%>% pmin(7),
    sd = ci(Score)[4],
    std = Score %>% sd())

level2_data_key_summary

# line + dot
level2_data_key_graph <- ggplot(level2_data_key_summary) +
  geom_pointrange( aes(x=reorder(Key, desc(Key)), y=meanScore, ymin=lowCI, ymax=highCI), colour="#2e86c1", alpha=0.9, size=0.8) +
  scale_y_reverse(lim=c(7,1)) + 
  coord_flip()

level2_data_key_graph

level2_data_key_graph + theme( # remove the vertical grid lines
          panel.background = element_blank(),
          panel.grid.major.y = element_blank() ,
          # explicitly set the horizontal lines (or they will disappear too)
          panel.grid.major.x = element_line( size=.1, color="gray" ),
          axis.title.x = element_blank(),
          axis.text.x=element_blank(),
          axis.ticks.x = element_blank(),
          axis.title.y = element_blank(),
          axis.text.y=element_blank(),
          axis.ticks.y = element_blank()
    )

ggsave("2level_easiness_key.pdf", width = 3, height = 8)


```
#### analysis

```{r warning=FALSE}
m = aov(Score ~ Level, data=level2_data_level_long) # make anova-type linear model
shapiro.test(residuals(m))
qqnorm(residuals(m)); qqline(residuals(m)) # Q-Q plot

# df has subjects (S), one within-Ss factor (X) w/levels (a,b,c), and continuous response (Y)
library(coin)
level2_data_level_long$ID = factor(level2_data_level_long$ID)
friedman_test(Score ~ Level | ID, data=level2_data_level_long, distribution="asymptotic")
friedman_effsize(Score ~ Level | ID, data=level2_data_level_long)

pairwise.wilcox.test(x = level2_data_level_long$Score, 
                     g = level2_data_level_long$Level, 
                     p.adjust.method = "holm", 
                     paired = TRUE)

m = aov(Score ~ Key, data=level2_data_key_long) # make anova-type linear model
shapiro.test(residuals(m))
qqnorm(residuals(m)); qqline(residuals(m)) # Q-Q plot

# df has subjects (S), one within-Ss factor (X) w/levels (a,b,c), and continuous response (Y)
library(coin)
level2_data_key_long$ID = factor(level2_data_key_long$ID)
friedman_test(Score ~ Key | ID, data=level2_data_key_long, distribution="asymptotic")
friedman_effsize(Score ~ Key | ID, data=level2_data_key_long)

pairwise.wilcox.test(x = level2_data_key_long$Score, 
                     g = level2_data_key_long$Key, 
                     p.adjust.method = "holm", 
                     paired = TRUE)

```

Main effect on Level: Full is easier than Light
Main effect on Key: (FJ) easier than (ASDL;), J easier than K


#### 3 level - easiness
```{r warning=FALSE}

level3_data_level <- level3_data %>%
  dplyr::select(ID, Light_easiness:Full_easiness)

colnames(level3_data_level) <- c("ID", "light", "medium", "full")

level3_data_level_long <- level3_data_level %>%
  pivot_longer(
    cols = light:full, # Selects columns that start with "Test"
    names_to = "Level",     # Name for the new column holding the original column names (e.g., Test1)
    values_to = "Score"        # Name for the new column holding the values (e.g., 85, 92)
  )

level3_data_key <- level3_data %>%
  dplyr::select(ID, A_easiness:Semicolon_easiness)

colnames(level3_data_key) <- c("ID", "A", "S", "D", "F", "J", "K", "L", "Semicolon")

level3_data_key_long <- level3_data_key %>%
  pivot_longer(
    cols = A:Semicolon, # Selects columns that start with "Test"
    names_to = "Key",     # Name for the new column holding the original column names (e.g., Test1)
    values_to = "Score"        # Name for the new column holding the values (e.g., 85, 92)
  )

level3_data_level_long$ID = factor(level3_data_level_long$ID)
level3_data_level_long$Level = factor(level3_data_level_long$Level, three_level_code)

boxplot(Score~Level,data=level3_data_level_long, main="level easiness",
   xlab="likert scale", ylab="level", horizontal=TRUE, outline = FALSE)


level3_data_level_summary <- level3_data_level_long %>%
  group_by(Level) %>%
  summarize(
    meanScore = Score %>% mean(na.rm=TRUE),
    lowCI = ci(Score)[2]%>% pmax(0),
    highCI = ci(Score)[3]%>% pmin(7),
    sd = ci(Score)[4],
    std = Score %>% sd())

level3_data_level_summary

# line + dot
level3_data_level_graph <- ggplot(level3_data_level_summary) +
  geom_pointrange( aes(x=reorder(Level, desc(Level)), y=meanScore, ymin=lowCI, ymax=highCI), colour="#2e86c1", alpha=0.9, size=0.8) +
  scale_y_reverse(lim=c(7,1)) + 
  coord_flip()

level3_data_level_graph

level3_data_level_graph + theme( # remove the vertical grid lines
          panel.background = element_blank(),
          panel.grid.major.y = element_blank() ,
          # explicitly set the horizontal lines (or they will disappear too)
          panel.grid.major.x = element_line( size=.1, color="gray" ),
          axis.title.x = element_blank(),
          axis.text.x=element_blank(),
          axis.ticks.x = element_blank(),
          axis.title.y = element_blank(),
          axis.text.y=element_blank(),
          axis.ticks.y = element_blank()
    )

ggsave("3level_easiness_level.pdf", width = 3, height = 3)


level3_data_key_long$ID = factor(level3_data_key_long$ID)
level3_data_key_long$Key = factor(level3_data_key_long$Key, key_code)

boxplot(Score~Key,data=level3_data_key_long, main="key easiness",
   xlab="likert scale", ylab="key", horizontal=TRUE, outline = FALSE)


level3_data_key_summary <- level3_data_key_long %>%
  group_by(Key) %>%
  summarize(
    meanScore = Score %>% mean(na.rm=TRUE),
    lowCI = ci(Score)[2]%>% pmax(0),
    highCI = ci(Score)[3]%>% pmin(7),
    sd = ci(Score)[4],
    std = Score %>% sd())

level3_data_key_summary

# line + dot
level3_data_key_graph <- ggplot(level3_data_key_summary) +
  geom_pointrange( aes(x=reorder(Key, desc(Key)), y=meanScore, ymin=lowCI, ymax=highCI), colour="#2e86c1", alpha=0.9, size=0.8) +
  scale_y_reverse(lim=c(7,1)) + 
  coord_flip()

level3_data_key_graph

level3_data_key_graph + theme( # remove the vertical grid lines
          panel.background = element_blank(),
          panel.grid.major.y = element_blank() ,
          # explicitly set the horizontal lines (or they will disappear too)
          panel.grid.major.x = element_line( size=.1, color="gray" ),
          axis.title.x = element_blank(),
          axis.text.x=element_blank(),
          axis.ticks.x = element_blank(),
          axis.title.y = element_blank(),
          axis.text.y=element_blank(),
          axis.ticks.y = element_blank()
    )

ggsave("3level_easiness_key.pdf", width = 3, height = 8)


```
#### analysis

```{r warning=FALSE}
m = aov(Score ~ Level, data=level3_data_level_long) # make anova-type linear model
shapiro.test(residuals(m))
qqnorm(residuals(m)); qqline(residuals(m)) # Q-Q plot

# df has subjects (S), one within-Ss factor (X) w/levels (a,b,c), and continuous response (Y)
library(coin)
level3_data_level_long$ID = factor(level3_data_level_long$ID)
friedman_test(Score ~ Level | ID, data=level3_data_level_long, distribution="asymptotic")
friedman_effsize(Score ~ Level | ID, data=level3_data_level_long)

pairwise.wilcox.test(x = level3_data_level_long$Score, 
                     g = level3_data_level_long$Level, 
                     p.adjust.method = "holm", 
                     paired = TRUE)

m = aov(Score ~ Key, data=level3_data_key_long) # make anova-type linear model
shapiro.test(residuals(m))
qqnorm(residuals(m)); qqline(residuals(m)) # Q-Q plot

# df has subjects (S), one within-Ss factor (X) w/levels (a,b,c), and continuous response (Y)
library(coin)
level3_data_key_long$ID = factor(level3_data_key_long$ID)
friedman_test(Score ~ Key | ID, data=level3_data_key_long, distribution="asymptotic")
friedman_effsize(Score ~ Key | ID, data=level3_data_key_long)

pairwise.wilcox.test(x = level3_data_key_long$Score, 
                     g = level3_data_key_long$Key, 
                     p.adjust.method = "holm", 
                     paired = TRUE)

```

Main effect on Level: Full is easier than light and medium
Main effect on Key: (FJ) is easier than (ASDKL;), K is easier than L



#### 4 level - easiness
```{r warning=FALSE}

level4_data_level <- level4_data %>%
  dplyr::select(ID, Light_easiness:Full_easiness)

colnames(level4_data_level) <- c("ID", "light", "mediumLow", "mediumHigh","full")

level4_data_level_long <- level4_data_level %>%
  pivot_longer(
    cols = light:full, # Selects columns that start with "Test"
    names_to = "Level",     # Name for the new column holding the original column names (e.g., Test1)
    values_to = "Score"        # Name for the new column holding the values (e.g., 85, 92)
  )

level4_data_key <- level4_data %>%
  dplyr::select(ID, A_easiness:Semicolon_easiness)

colnames(level4_data_key) <- c("ID", "A", "S", "D", "F", "J", "K", "L", "Semicolon")

level4_data_key_long <- level4_data_key %>%
  pivot_longer(
    cols = A:Semicolon, # Selects columns that start with "Test"
    names_to = "Key",     # Name for the new column holding the original column names (e.g., Test1)
    values_to = "Score"        # Name for the new column holding the values (e.g., 85, 92)
  )

level4_data_level_long$ID = factor(level4_data_level_long$ID)
level4_data_level_long$Level = factor(level4_data_level_long$Level, four_level_code)

boxplot(Score~Level,data=level4_data_level_long, main="level easiness",
   xlab="likert scale", ylab="level", horizontal=TRUE, outline = FALSE)


level4_data_level_summary <- level4_data_level_long %>%
  group_by(Level) %>%
  summarize(
    meanScore = Score %>% mean(na.rm=TRUE),
    lowCI = ci(Score)[2]%>% pmax(0),
    highCI = ci(Score)[3]%>% pmin(7),
    sd = ci(Score)[4],
    std = Score %>% sd())

level4_data_level_summary

# line + dot
level4_data_level_graph <- ggplot(level4_data_level_summary) +
  geom_pointrange( aes(x=reorder(Level, desc(Level)), y=meanScore, ymin=lowCI, ymax=highCI), colour="#2e86c1", alpha=0.9, size=0.8) +
  scale_y_reverse(lim=c(7,1)) + 
  coord_flip()

level4_data_level_graph

level4_data_level_graph + theme( # remove the vertical grid lines
          panel.background = element_blank(),
          panel.grid.major.y = element_blank() ,
          # explicitly set the horizontal lines (or they will disappear too)
          panel.grid.major.x = element_line( size=.1, color="gray" ),
          axis.title.x = element_blank(),
          axis.text.x=element_blank(),
          axis.ticks.x = element_blank(),
          axis.title.y = element_blank(),
          axis.text.y=element_blank(),
          axis.ticks.y = element_blank()
    )

ggsave("4level_easiness_level.pdf", width = 3, height = 4)


level4_data_key_long$ID = factor(level4_data_key_long$ID)
level4_data_key_long$Key = factor(level4_data_key_long$Key, key_code)

boxplot(Score~Key,data=level4_data_key_long, main="key easiness",
   xlab="likert scale", ylab="key", horizontal=TRUE, outline = FALSE)


level4_data_key_summary <- level4_data_key_long %>%
  group_by(Key) %>%
  summarize(
    meanScore = Score %>% mean(na.rm=TRUE),
    lowCI = ci(Score)[2]%>% pmax(0),
    highCI = ci(Score)[3]%>% pmin(7),
    sd = ci(Score)[4],
    std = Score %>% sd())

level4_data_key_summary

# line + dot
level4_data_key_graph <- ggplot(level4_data_key_summary) +
  geom_pointrange( aes(x=reorder(Key, desc(Key)), y=meanScore, ymin=lowCI, ymax=highCI), colour="#2e86c1", alpha=0.9, size=0.8) +
  scale_y_reverse(lim=c(7,1)) + 
  coord_flip()

level4_data_key_graph

level4_data_key_graph + theme( # remove the vertical grid lines
          panel.background = element_blank(),
          panel.grid.major.y = element_blank() ,
          # explicitly set the horizontal lines (or they will disappear too)
          panel.grid.major.x = element_line( size=.1, color="gray" ),
          axis.title.x = element_blank(),
          axis.text.x=element_blank(),
          axis.ticks.x = element_blank(),
          axis.title.y = element_blank(),
          axis.text.y=element_blank(),
          axis.ticks.y = element_blank()
    )

ggsave("4level_easiness_key.pdf", width = 3, height = 8)


```
#### analysis

```{r warning=FALSE}
m = aov(Score ~ Level, data=level4_data_level_long) # make anova-type linear model
shapiro.test(residuals(m))
qqnorm(residuals(m)); qqline(residuals(m)) # Q-Q plot

# df has subjects (S), one within-Ss factor (X) w/levels (a,b,c), and continuous response (Y)
library(coin)
level4_data_level_long$ID = factor(level4_data_level_long$ID)
friedman_test(Score ~ Level | ID, data=level4_data_level_long, distribution="asymptotic")
friedman_effsize(Score ~ Level | ID, data=level4_data_level_long)

pairwise.wilcox.test(x = level4_data_level_long$Score, 
                     g = level4_data_level_long$Level, 
                     p.adjust.method = "holm", 
                     paired = TRUE)

m = aov(Score ~ Key, data=level4_data_key_long) # make anova-type linear model
shapiro.test(residuals(m))
qqnorm(residuals(m)); qqline(residuals(m)) # Q-Q plot

# df has subjects (S), one within-Ss factor (X) w/levels (a,b,c), and continuous response (Y)
library(coin)
level4_data_key_long$ID = factor(level4_data_key_long$ID)
friedman_test(Score ~ Key | ID, data=level4_data_key_long, distribution="asymptotic")
friedman_effsize(Score ~ Key | ID, data=level4_data_key_long)

pairwise.wilcox.test(x = level4_data_key_long$Score, 
                     g = level4_data_key_long$Key, 
                     p.adjust.method = "holm", 
                     paired = TRUE)

```

Main effect on Level: full is easier than light, mediumLow, and mediumHigh; Light is easier than mediumLow, and mediumHigh
Main effect on Key: (FJ) is easier than (ASDKL;)




