---
title: "trial results"
author: "Allen Yeh"
output:
  html_document: default
  pdf_document: default
---

```
```

```{r warning=FALSE}
library(tidyverse)
library(gmodels)
library(rstatix)
library(ggplot2)
library(ez)
```

### Import data

#### Read the csv file and claim the data type
```{r}
 
participant_id = c("1", "2", "3", "4", "5", "6", "7", "8", "9", "10", "11", "12", "13", "14", "15", "16", "17", "18", "19", "20", "21", "23", "24", "40")

key_code = c("A", "S", "D", "F", "J", "K", "L", "Semicolon")

level_code = c("full", "mediumHigh", "mediumLow", "medium", "light")

# Initialize an empty data frame
trial_log = NULL

for (x in participant_id) {
  filename <- paste("./../results/", x, ".csv", sep="")
  trial_user_log <- read_csv(filename, col_types = cols(
    id = col_factor(levels = participant_id),
    level = col_integer(),
    block = col_factor(levels = c("0", "1", "2", "3", "4", "5")),
    trial = col_integer(),
    levelCounts = col_factor(levels = c("2", "3", "4")),
    targetKey = col_factor(levels = key_code),
    targetLevel = col_factor(levels = level_code),
    pressedLevel = col_factor(levels = level_code),
    pressedRaw = col_integer(),
    isSuccessful = col_logical(),
    startTime = col_double(),
    endTime = col_double(),
    time = col_double(),
  )) %>% filter(block %in% c("1", "2", "3", "4", "5"))
  trial_log = bind_rows(trial_log,trial_user_log)
}


```

### functions

```{r warning=FALSE}
percent <- function(num, digits = 2, ...) {      
  percentage <-formatC(num * 100, format = "f", digits = digits, ...)
  
  # appending "%" symbol at the end of
  # calculate percentage value
  paste0(percentage, "%")
}
```

### Total

#### block accuracy
```{r warning=FALSE}

log_block_accuracy <- trial_log %>%
  group_by(id, levelCounts, block) %>%
  summarize(
    accuracy_ave = sum(isSuccessful) / n(),
    n_trials = n()
  ) %>%
  ungroup() %>%
  arrange(id, levelCounts, block)

log_accuracy_summary <- log_block_accuracy  %>%
  group_by(block, levelCounts) %>%
  summarize(
    meanAccuracy = accuracy_ave %>% mean(na.rm=TRUE),
    lowCIAccuracy = ci(accuracy_ave)[2] %>% pmax(0),
    highCIAccuracy = ci(accuracy_ave)[3] %>% pmin(1),
    sdAccuracy = ci(accuracy_ave)[4],
    stdAccuracy = sd(accuracy_ave)) %>%
  ungroup() %>%
  arrange(block, levelCounts)

log_accuracy_summary

pd <- position_dodge(width = 0.3)
log_accuracy_summary %>% ggplot(
  aes(
    x = block,
    y = meanAccuracy,
    ymin = lowCIAccuracy,
    ymax = highCIAccuracy,
    color = levelCounts
  )
) +
  geom_pointrange(position = pd) 

m = aov(accuracy_ave ~ block*levelCounts, data=log_block_accuracy) # make anova-type linear model
shapiro.test(residuals(m))
qqnorm(residuals(m)); qqline(residuals(m)) # Q-Q plot

library(ARTool)
log_block_accuracy$id = factor(log_block_accuracy$id)
m = art(accuracy_ave ~ block*levelCounts + (1|id), data=log_block_accuracy) # subjects (S) as random effect
anova(m)

# art.con(m, "block")

```

No effect on block, no learning effect. Including all trials.

#### levelCount accuracy
```{r warning=FALSE}
log_accuracy <- trial_log %>%
  group_by(id, levelCounts) %>%
  summarize(
    accuracy_ave = sum(isSuccessful) / n(),
    n_trials = n()
  ) %>%
  ungroup() %>%
  arrange(id, levelCounts)

log_accuracy_summary <- log_accuracy  %>%
  group_by(levelCounts) %>%
  summarize(
    meanAccuracy = accuracy_ave %>% mean(na.rm=TRUE),
    lowCIAccuracy = ci(accuracy_ave)[2] %>% pmax(0),
    highCIAccuracy = ci(accuracy_ave)[3] %>% pmin(1),
    sdAccuracy = ci(accuracy_ave)[4],
    stdAccuracy = sd(accuracy_ave)) %>%
  ungroup() %>%
  arrange(levelCounts)

log_accuracy_summary

# pd <- position_dodge(width = 0.3)
# log_accuracy_summary %>% ggplot(
#   aes(
#     x = levelCounts,
#     y = meanAccuracy,
#     ymin = lowCIAccuracy,
#     ymax = highCIAccuracy
#   )
# ) +
#   geom_pointrange(position = pd) 

# line + dot
accuracy_graph <- ggplot(log_accuracy_summary) +
  geom_pointrange( aes(x=reorder(levelCounts, desc(levelCounts)), y=meanAccuracy, ymin=lowCIAccuracy, ymax=highCIAccuracy), colour="#28b463", alpha=0.9, size=0.8) +
  scale_y_reverse(lim=c(1.0,0.3)) + 
  coord_flip()

accuracy_graph

accuracy_graph + theme( # remove the vertical grid lines
          panel.background = element_blank(),
          panel.grid.major.y = element_blank() ,
          # explicitly set the horizontal lines (or they will disappear too)
          panel.grid.major.x = element_line( size=.1, color="gray" ),
          axis.title.x = element_blank(),
          axis.text.x=element_blank(),
          axis.ticks.x = element_blank(),
          axis.title.y = element_blank(),
          axis.text.y=element_blank(),
          axis.ticks.y = element_blank()
    )

ggsave("accuracy_levels.pdf", width = 4, height = 3)

m = aov(accuracy_ave ~ levelCounts, data=log_accuracy) # make anova-type linear model
shapiro.test(residuals(m))
qqnorm(residuals(m)); qqline(residuals(m)) # Q-Q plot

library(ez) # for ezANOVA
log_accuracy$id = factor(log_accuracy$id)
m = ezANOVA(dv=accuracy_ave, within=c(levelCounts), wid=id, data=log_accuracy)
m$Mauchly # p<.05 indicates a sphericity violation
m$ANOVA # use if no violation

#library(reshape2) # for dcast
#df2 <- dcast(log_accuracy, id ~ levelCounts, value.var="accuracy_ave") # make wide-format table
#ab = t.test(df2$"2", df2$"3", paired=TRUE, var.equal=TRUE) # a vs. b
#ac = t.test(df2$"2", df2$"4", paired=TRUE, var.equal=TRUE) # a vs. c
#bc = t.test(df2$"3", df2$"4", paired=TRUE, var.equal=TRUE) # b vs. c
#p.adjust(c(ab$p.value, ac$p.value, bc$p.value), method="holm")

pairwise.t.test(log_accuracy$accuracy_ave, log_accuracy$levelCounts, paired=TRUE, p.adjust="holm")

```

2 levels is better than 3 and 4 levels. 
3 levels is better than 4 levels.


#### levelCount time
```{r warning=FALSE}
log_time_filtered <- trial_log %>% 
  group_by(id) %>% 
  mutate(IQR = IQR(time),
            O_upper = quantile(time, probs=c( .75), na.rm = FALSE)+1.5*IQR,  
            O_lower = quantile(time, probs=c( .25), na.rm = FALSE)-1.5*IQR  
  ) %>% 
  filter(O_lower <= time & time <= O_upper)

log_time <- log_time_filtered %>%
  group_by(id, levelCounts) %>%
  summarize(
    time_ave = sum(time) / n(),
    n_trials = n()
  ) %>%
  ungroup() %>%
  arrange(id, levelCounts)

log_time_summary <- log_time  %>%
  group_by(levelCounts) %>%
  summarize(
    meanTime = time_ave %>% mean(na.rm=TRUE),
    lowCITime = ci(time_ave)[2] %>% pmax(0),
    highCITime = ci(time_ave)[3],
    sdTime = ci(time_ave)[4],
    stdTime = sd(time_ave)) %>%
  ungroup() %>%
  arrange(levelCounts)

log_time_summary

# pd <- position_dodge(width = 0.3)
# log_time_summary %>% ggplot(
#   aes(
#     x = levelCounts,
#     y = meanTime,
#     ymin = lowCITime,
#     ymax = highCITime
#   )
# ) +
#   geom_pointrange(position = pd) 

# line + dot
time_graph <- ggplot(log_time_summary) +
  geom_pointrange( aes(x=reorder(levelCounts, desc(levelCounts)), y=meanTime, ymin=lowCITime, ymax=highCITime), colour="#707b7c", alpha=0.9, size=0.8) +
  scale_y_continuous(lim=c(900,1800)) + 
  coord_flip()

time_graph

time_graph + theme( # remove the vertical grid lines
          panel.background = element_blank(),
          panel.grid.major.y = element_blank() ,
          # explicitly set the horizontal lines (or they will disappear too)
          panel.grid.major.x = element_line( size=.1, color="gray" ),
          axis.title.x = element_blank(),
          axis.text.x=element_blank(),
          axis.ticks.x = element_blank(),
          axis.title.y = element_blank(),
          axis.text.y=element_blank(),
          axis.ticks.y = element_blank()
    )

ggsave("time_levels.pdf", width = 4, height = 3)

m = aov(time_ave ~ levelCounts, data=log_time) # make anova-type linear model
shapiro.test(residuals(m))
qqnorm(residuals(m)); qqline(residuals(m)) # Q-Q plot

# df has subjects (S), one within-Ss factor (X) w/levels (a,b,c), and continuous response (Y)
library(coin)
log_time$id = factor(log_time$id)
friedman_test(time_ave ~ levelCounts | id, data=log_time, distribution="asymptotic")

library(reshape2) # for dcast
df2 <- dcast(log_time, id ~ levelCounts, value.var="time_ave") # make wide-format table
ab = wilcox.test(df2$"2", df2$"3", paired=TRUE) # a vs. b
ac = wilcox.test(df2$"2", df2$"4", paired=TRUE) # a vs. c
bc = wilcox.test(df2$"3", df2$"4", paired=TRUE) # b vs. c
p.adjust(c(ab$p.value, ac$p.value, bc$p.value), method="holm")



pairwise.t.test(log_time$time_ave, log_time$levelCounts, paired=TRUE, p.adjust="holm")

```

2 levels is faster than 3 and 4 levels. 
3 levels is faster than 4 levels.


### 2 level

#### accuracy
```{r warning=FALSE}
log_twolevel_accuracy <- trial_log %>%
  filter(levelCounts == c("2")) %>%
  group_by(id, targetLevel, targetKey) %>%
  summarize(
    accuracy_ave = sum(isSuccessful) / n(),
    n_trials = n()
  ) %>%
  ungroup() %>%
  arrange(id, targetLevel, targetKey)

log_twolevel_accuracy_summary <- log_twolevel_accuracy  %>%
  group_by(targetLevel, targetKey) %>%
  summarize(
    meanAccuracy = accuracy_ave %>% mean(na.rm=TRUE),
    lowCIAccuracy = ci(accuracy_ave)[2] %>% pmax(0),
    highCIAccuracy = ci(accuracy_ave)[3] %>% pmin(1),
    sdAccuracy = ci(accuracy_ave)[4],
    stdAccuracy = sd(accuracy_ave)) %>%
  ungroup() %>%
  arrange(targetLevel, targetKey)

log_twolevel_accuracy_summary

pd <- position_dodge(width = 0.3)
log_twolevel_accuracy_summary %>% ggplot(
  aes(
    x = targetKey,
    y = meanAccuracy,
    ymin = lowCIAccuracy,
    ymax = highCIAccuracy,
    color = targetLevel
  )
) +
  geom_pointrange(position = pd) 

m = aov(accuracy_ave ~ targetLevel*targetKey, data=log_twolevel_accuracy) # make anova-type linear model
shapiro.test(residuals(m))
qqnorm(residuals(m)); qqline(residuals(m)) # Q-Q plot

library(ARTool)
log_twolevel_accuracy$id = factor(log_twolevel_accuracy$id) # Subject id must be nominal
m = art(accuracy_ave ~ targetLevel*targetKey + (1|id), data=log_twolevel_accuracy) # subjects (S) as random effect
anova(m)

art.con(m, "targetLevel")

log_twolevel_accuracy_summary_level <- log_twolevel_accuracy  %>%
  group_by(targetLevel) %>%
  summarize(
    meanAccuracy = accuracy_ave %>% mean(na.rm=TRUE),
    lowCIAccuracy = ci(accuracy_ave)[2] %>% pmax(0),
    highCIAccuracy = ci(accuracy_ave)[3] %>% pmin(1),
    sdAccuracy = ci(accuracy_ave)[4],
    stdAccuracy = sd(accuracy_ave)) %>%
  ungroup() %>%
  arrange(targetLevel)

log_twolevel_accuracy_summary_level

# line + dot (levels)
twolevel_accuracy_level <- ggplot(log_twolevel_accuracy_summary_level) +
  geom_pointrange( aes(x=reorder(targetLevel, desc(targetLevel)), y=meanAccuracy, ymin=lowCIAccuracy, ymax=highCIAccuracy), colour="#28b463", alpha=0.9, size=0.8) +
  scale_y_reverse(lim=c(1.0,0.3)) + 
  coord_flip()

twolevel_accuracy_level

twolevel_accuracy_level + theme( # remove the vertical grid lines
          panel.background = element_blank(),
          panel.grid.major.y = element_blank() ,
          # explicitly set the horizontal lines (or they will disappear too)
          panel.grid.major.x = element_line( size=.1, color="gray" ),
          axis.title.x = element_blank(),
          axis.text.x=element_blank(),
          axis.ticks.x = element_blank(),
          axis.title.y = element_blank(),
          axis.text.y=element_blank(),
          axis.ticks.y = element_blank()
    )

ggsave("accuracy_twolevel_level.pdf", width = 4, height = 2)

log_twolevel_accuracy_summary_key <- log_twolevel_accuracy  %>%
  group_by(targetKey) %>%
  summarize(
    meanAccuracy = accuracy_ave %>% mean(na.rm=TRUE),
    lowCIAccuracy = ci(accuracy_ave)[2] %>% pmax(0),
    highCIAccuracy = ci(accuracy_ave)[3] %>% pmin(1),
    sdAccuracy = ci(accuracy_ave)[4],
    stdAccuracy = sd(accuracy_ave)) %>%
  ungroup() %>%
  arrange(targetKey)

log_twolevel_accuracy_summary_key

# line + dot (key)
twolevel_accuracy_key <- ggplot(log_twolevel_accuracy_summary_key) +
  geom_pointrange( aes(x=reorder(targetKey, desc(targetKey)), y=meanAccuracy, ymin=lowCIAccuracy, ymax=highCIAccuracy), colour="#28b463", alpha=0.9, size=0.8) +
  scale_y_reverse(lim=c(1.0,0.3)) + 
  coord_flip()

twolevel_accuracy_key

twolevel_accuracy_key + theme( # remove the vertical grid lines
          panel.background = element_blank(),
          panel.grid.major.y = element_blank() ,
          # explicitly set the horizontal lines (or they will disappear too)
          panel.grid.major.x = element_line( size=.1, color="gray" ),
          axis.title.x = element_blank(),
          axis.text.x=element_blank(),
          axis.ticks.x = element_blank(),
          axis.title.y = element_blank(),
          axis.text.y=element_blank(),
          axis.ticks.y = element_blank()
    )

ggsave("accuracy_twolevel_key.pdf", width = 4, height = 8)
```

Main effect on targetLevel: Full has higher accuracy.



#### actual press - user threshold
```{r warning=FALSE}
log_twolevel <- trial_log %>%
  filter(levelCounts == c("2"))

log_twolevel_user <- log_twolevel %>% 
  group_by(id, targetLevel) %>% 
  mutate(
    pressRawPercent = pressedRaw * 100.0 / 255.0,
  ) %>% 
  ungroup()

log_twolevel_user_quantile <- log_twolevel_user%>%
  group_by(id, targetLevel) %>%
  summarize(
    lower_outlier = boxplot.stats(pressedRaw)$stats[c(1)],
    lower = boxplot.stats(pressedRaw)$stats[c(2)],
    median = boxplot.stats(pressedRaw)$stats[c(3)],
    upper = boxplot.stats(pressedRaw)$stats[c(4)],
    upper_outlier = boxplot.stats(pressedRaw)$stats[c(5)],
  ) %>%
  ungroup() %>%
  arrange(id, targetLevel)

library(reshape2) # for dcast

melted_threshold <- melt(log_twolevel_user_quantile, id.vars = c("id", "targetLevel"), measure.vars = c("lower_outlier", "lower", "median", "upper", "upper_outlier"))

#melted_threshold

cast_threshold <- dcast(melted_threshold, id~targetLevel * variable, value.var="value")%>%
  group_by(id) %>%
  mutate(
    full_threshold = median(c(full_lower_outlier, full_lower,light_upper, light_upper_outlier))
  ) %>%
  ungroup()

#cast_threshold

log_twolevel_user <- merge(log_twolevel_user, cast_threshold,
                          by = 'id', all = TRUE)

log_twolevel_user <- log_twolevel_user %>% 
  mutate(
    pressLevel_user = ifelse(pressedRaw >= full_threshold, "full", "light"),
    isSuccessful_user = (targetLevel == pressLevel_user)
  )

#log_twolevel_user


log_twolevel_user %>% ggplot(
  aes(
    x = targetLevel,
    y = pressRawPercent
  )
) + 
  geom_violin() + 
  geom_boxplot(width = 0.03, outlier.shape = 1, , outlier.alpha = 0.3)

```

##### confusion table
```{r warning=FALSE}
library(cvms)
conf_mat <- confusion_matrix(targets = log_twolevel_user$targetLevel,
                             predictions = log_twolevel_user$pressedLevel)

conf_mat

plot_confusion_matrix(conf_mat$`Confusion Matrix`[[1]],
  add_normalized = FALSE,
  add_row_percentages = FALSE)

conf_mat <- confusion_matrix(targets = log_twolevel_user$targetLevel,
                             predictions = log_twolevel_user$pressLevel_user)

conf_mat

plot_confusion_matrix(conf_mat$`Confusion Matrix`[[1]],
  add_normalized = FALSE,
  add_row_percentages = FALSE)

```


#### time
```{r warning=FALSE}
log_twoLevel_time <- log_time_filtered%>%
  filter(levelCounts == c("2")) %>%
  group_by(id, targetLevel, targetKey) %>%
  summarize(
    time_ave = sum(time) / n(),
    n_trials = n()
  ) %>%
  ungroup() %>%
  arrange(id, targetLevel, targetKey)

log_twoLevel_time_summary <- log_twoLevel_time  %>%
  group_by(targetLevel, targetKey) %>%
  summarize(
    meanTime = time_ave %>% mean(na.rm=TRUE),
    lowCITime = ci(time_ave)[2] %>% pmax(0),
    highCITime = ci(time_ave)[3],
    sdTime = ci(time_ave)[4],
    stdTime = sd(time_ave)) %>%
  ungroup() %>%
  arrange(targetLevel, targetKey)

log_twoLevel_time_summary

pd <- position_dodge(width = 0.3)
log_twoLevel_time_summary %>% ggplot(
  aes(
    x = targetKey,
    y = meanTime,
    ymin = lowCITime,
    ymax = highCITime,
    color = targetLevel
  )
) +
  geom_pointrange(position = pd) 

m = aov(time_ave ~ targetLevel*targetKey, data=log_twoLevel_time) # make anova-type linear model
shapiro.test(residuals(m))
qqnorm(residuals(m)); qqline(residuals(m)) # Q-Q plot

library(ARTool)
log_twoLevel_time$id = factor(log_twoLevel_time$id) # Subject id must be nominal
m = art(time_ave ~ targetLevel*targetKey + (1|id), data=log_twoLevel_time) # subjects (S) as random effect
anova(m)

#art.con(m, "targetLevel")
art.con(m, "targetKey")


log_twoLevel_time_summary_level <- log_twoLevel_time  %>%
  group_by(targetLevel) %>%
  summarize(
    meanTime = time_ave %>% mean(na.rm=TRUE),
    lowCITime = ci(time_ave)[2] %>% pmax(0),
    highCITime = ci(time_ave)[3],
    sdTime = ci(time_ave)[4],
    stdTime = sd(time_ave)) %>%
  ungroup() %>%
  arrange(targetLevel)

log_twoLevel_time_summary_level

# line + dot (levels)
twolevel_time_level <- ggplot(log_twoLevel_time_summary_level) +
  geom_pointrange( aes(x=reorder(targetLevel, desc(targetLevel)), y=meanTime, ymin=lowCITime, ymax=highCITime), colour="#707b7c", alpha=0.9, size=0.8) +
  scale_y_continuous(lim=c(900,1800)) + 
  coord_flip()

twolevel_time_level

twolevel_time_level + theme( # remove the vertical grid lines
          panel.background = element_blank(),
          panel.grid.major.y = element_blank() ,
          # explicitly set the horizontal lines (or they will disappear too)
          panel.grid.major.x = element_line( size=.1, color="gray" ),
          axis.title.x = element_blank(),
          axis.text.x=element_blank(),
          axis.ticks.x = element_blank(),
          axis.title.y = element_blank(),
          axis.text.y=element_blank(),
          axis.ticks.y = element_blank()
    )

ggsave("time_twolevel_level.pdf", width = 4, height = 2)

log_twoLevel_time_summary_key <- log_twoLevel_time  %>%
  group_by(targetKey) %>%
  summarize(
    meanTime = time_ave %>% mean(na.rm=TRUE),
    lowCITime = ci(time_ave)[2] %>% pmax(0),
    highCITime = ci(time_ave)[3],
    sdTime = ci(time_ave)[4],
    stdTime = sd(time_ave)) %>%
  ungroup() %>%
  arrange(targetKey)

log_twoLevel_time_summary_key

# line + dot (key)
twolevel_time_key <- ggplot(log_twoLevel_time_summary_key) +
  geom_pointrange( aes(x=reorder(targetKey, desc(targetKey)), y=meanTime, ymin=lowCITime, ymax=highCITime), colour="#707b7c", alpha=0.9, size=0.8) +
  scale_y_continuous(lim=c(900,1800)) + 
  coord_flip()

twolevel_time_key

twolevel_time_key + theme( # remove the vertical grid lines
          panel.background = element_blank(),
          panel.grid.major.y = element_blank() ,
          # explicitly set the horizontal lines (or they will disappear too)
          panel.grid.major.x = element_line( size=.1, color="gray" ),
          axis.title.x = element_blank(),
          axis.text.x=element_blank(),
          axis.ticks.x = element_blank(),
          axis.title.y = element_blank(),
          axis.text.y=element_blank(),
          axis.ticks.y = element_blank()
    )

ggsave("time_twolevel_key.pdf", width = 4, height = 8)
```

Main effect on keys: "TODO"

### 3 level

#### accuracy
```{r warning=FALSE}
log_threelevel_accuracy <- trial_log %>%
  filter(levelCounts == c("3")) %>%
  group_by(id, targetLevel, targetKey) %>%
  summarize(
    accuracy_ave = sum(isSuccessful) / n(),
    n_trials = n()
  ) %>%
  ungroup() %>%
  arrange(id, targetLevel, targetKey)

log_threelevel_accuracy_summary <- log_threelevel_accuracy  %>%
  group_by(targetLevel, targetKey) %>%
  summarize(
    meanAccuracy = accuracy_ave %>% mean(na.rm=TRUE),
    lowCIAccuracy = ci(accuracy_ave)[2] %>% pmax(0),
    highCIAccuracy = ci(accuracy_ave)[3] %>% pmin(1),
    sdAccuracy = ci(accuracy_ave)[4],
    stdAccuracy = sd(accuracy_ave)) %>%
  ungroup() %>%
  arrange(targetLevel, targetKey)

log_threelevel_accuracy_summary

pd <- position_dodge(width = 0.3)
log_threelevel_accuracy_summary %>% ggplot(
  aes(
    x = targetKey,
    y = meanAccuracy,
    ymin = lowCIAccuracy,
    ymax = highCIAccuracy,
    color = targetLevel
  )
) +
  geom_pointrange(position = pd) 

m = aov(accuracy_ave ~ targetLevel*targetKey, data=log_threelevel_accuracy) # make anova-type linear model
shapiro.test(residuals(m))
qqnorm(residuals(m)); qqline(residuals(m)) # Q-Q plot

library(ARTool)
log_threelevel_accuracy$id = factor(log_threelevel_accuracy$id) # Subject id must be nominal
m = art(accuracy_ave ~ targetLevel*targetKey + (1|id), data=log_threelevel_accuracy) # subjects (S) as random effect
anova(m)

art.con(m, "targetLevel")
art.con(m, "targetKey")
# art.con(m, "targetLevel:targetKey")

log_threelevel_accuracy_summary_level <- log_threelevel_accuracy  %>%
  group_by(targetLevel) %>%
  summarize(
    meanAccuracy = accuracy_ave %>% mean(na.rm=TRUE),
    lowCIAccuracy = ci(accuracy_ave)[2] %>% pmax(0),
    highCIAccuracy = ci(accuracy_ave)[3] %>% pmin(1),
    sdAccuracy = ci(accuracy_ave)[4],
    stdAccuracy = sd(accuracy_ave)) %>%
  ungroup() %>%
  arrange(targetLevel)

log_threelevel_accuracy_summary_level

# line + dot (levels)
threelevel_accuracy_level <- ggplot(log_threelevel_accuracy_summary_level) +
  geom_pointrange( aes(x=reorder(targetLevel, desc(targetLevel)), y=meanAccuracy, ymin=lowCIAccuracy, ymax=highCIAccuracy), colour="#28b463", alpha=0.9, size=0.8) +
  scale_y_reverse(lim=c(1.0,0.3)) + 
  coord_flip()

threelevel_accuracy_level

threelevel_accuracy_level + theme( # remove the vertical grid lines
          panel.background = element_blank(),
          panel.grid.major.y = element_blank() ,
          # explicitly set the horizontal lines (or they will disappear too)
          panel.grid.major.x = element_line( size=.1, color="gray" ),
          axis.title.x = element_blank(),
          axis.text.x=element_blank(),
          axis.ticks.x = element_blank(),
          axis.title.y = element_blank(),
          axis.text.y=element_blank(),
          axis.ticks.y = element_blank()
    )

ggsave("accuracy_threelevel_level.pdf", width = 4, height = 3)

log_threelevel_accuracy_summary_key <- log_threelevel_accuracy  %>%
  group_by(targetKey) %>%
  summarize(
    meanAccuracy = accuracy_ave %>% mean(na.rm=TRUE),
    lowCIAccuracy = ci(accuracy_ave)[2] %>% pmax(0),
    highCIAccuracy = ci(accuracy_ave)[3] %>% pmin(1),
    sdAccuracy = ci(accuracy_ave)[4],
    stdAccuracy = sd(accuracy_ave)) %>%
  ungroup() %>%
  arrange(targetKey)

log_threelevel_accuracy_summary_key

# line + dot (key)
threelevel_accuracy_key <- ggplot(log_threelevel_accuracy_summary_key) +
  geom_pointrange( aes(x=reorder(targetKey, desc(targetKey)), y=meanAccuracy, ymin=lowCIAccuracy, ymax=highCIAccuracy), colour="#28b463", alpha=0.9, size=0.8) +
  scale_y_reverse(lim=c(1.0,0.3)) + 
  coord_flip()

threelevel_accuracy_key

threelevel_accuracy_key + theme( # remove the vertical grid lines
          panel.background = element_blank(),
          panel.grid.major.y = element_blank() ,
          # explicitly set the horizontal lines (or they will disappear too)
          panel.grid.major.x = element_line( size=.1, color="gray" ),
          axis.title.x = element_blank(),
          axis.text.x=element_blank(),
          axis.ticks.x = element_blank(),
          axis.title.y = element_blank(),
          axis.text.y=element_blank(),
          axis.ticks.y = element_blank()
    )

ggsave("accuracy_threelevel_key.pdf", width = 4, height = 8)
```

Main effect on targetLevel: Full has higher accuracy then medium and light; Medium has higher accuracy then light.
Main effect on targetKey: J has higher accuracy than A, S, D, F, L, Semicolon
Interaction: "TODO"

#### actual press - user threshold
```{r warning=FALSE}

log_threelevel <- trial_log %>%
  filter(levelCounts == c("3"))

log_threelevel_user <- log_threelevel %>% 
  group_by(id, targetLevel) %>% 
  mutate(
    pressRawPercent = pressedRaw * 100.0 / 255.0,
  ) %>% 
  ungroup()

log_threelevel_user_quantile <- log_threelevel_user%>%
  group_by(id, targetLevel) %>%
  summarize(
    lower_outlier = boxplot.stats(pressedRaw)$stats[c(1)],
    lower = boxplot.stats(pressedRaw)$stats[c(2)],
    median = boxplot.stats(pressedRaw)$stats[c(3)],
    upper = boxplot.stats(pressedRaw)$stats[c(4)],
    upper_outlier = boxplot.stats(pressedRaw)$stats[c(5)],
  ) %>%
  ungroup() %>%
  arrange(id, targetLevel)

library(reshape2) # for dcast

melted_threshold <- melt(log_threelevel_user_quantile, id.vars = c("id", "targetLevel"), measure.vars = c("lower_outlier", "lower", "median", "upper", "upper_outlier"))
cast_threshold <- dcast(melted_threshold, id~targetLevel * variable, value.var="value") %>% 
  group_by(id) %>%
  mutate(
    full_threshold =  median(c(full_lower_outlier, full_lower,medium_upper, medium_upper_outlier)),
    medium_threshold =  median(c(medium_lower_outlier, medium_lower,light_upper, light_upper_outlier)),
  ) %>%
  ungroup()

log_threelevel_user <- merge(log_threelevel_user, cast_threshold,
                          by = 'id', all = TRUE)

log_threelevel_user <- log_threelevel_user %>% 
  mutate(
    pressLevel_user = ifelse(pressedRaw >= full_threshold, "full", ifelse(pressedRaw >= medium_threshold, "medium", "light")),
    isSuccessful_user = (targetLevel == pressLevel_user)
  )


log_threelevel_user %>% ggplot(
  aes(
    x = targetLevel,
    y = pressRawPercent
  )
) + 
  geom_violin() + 
  geom_boxplot(width = 0.03, outlier.shape = 1, , outlier.alpha = 0.3)

```


##### confusion table
```{r warning=FALSE}
library(cvms)
conf_mat <- confusion_matrix(targets = log_threelevel_user$targetLevel,
                             predictions = log_threelevel_user$pressedLevel)

conf_mat

plot_confusion_matrix(conf_mat$`Confusion Matrix`[[1]],
  add_normalized = FALSE,
  add_row_percentages = FALSE,
  class_order = c("full", "medium", "light"))

conf_mat <- confusion_matrix(targets = log_threelevel_user$targetLevel,
                             predictions = log_threelevel_user$pressLevel_user)

conf_mat

plot_confusion_matrix(conf_mat$`Confusion Matrix`[[1]],
  add_normalized = FALSE,
  add_row_percentages = FALSE,
  class_order = c("full", "medium", "light"))

```

#### time
```{r warning=FALSE}
log_threeLevel_time <- log_time_filtered%>%
  filter(levelCounts == c("3")) %>%
  group_by(id, targetLevel, targetKey) %>%
  summarize(
    time_ave = sum(time) / n(),
    n_trials = n()
  ) %>%
  ungroup() %>%
  arrange(id, targetLevel, targetKey)

log_threeLevel_time_summary <- log_threeLevel_time  %>%
  group_by(targetLevel, targetKey) %>%
  summarize(
    meanTime = time_ave %>% mean(na.rm=TRUE),
    lowCITime = ci(time_ave)[2] %>% pmax(0),
    highCITime = ci(time_ave)[3],
    sdTime = ci(time_ave)[4],
    stdTime = sd(time_ave)) %>%
  ungroup() %>%
  arrange(targetLevel, targetKey)

log_threeLevel_time_summary

pd <- position_dodge(width = 0.3)
log_threeLevel_time_summary %>% ggplot(
  aes(
    x = targetKey,
    y = meanTime,
    ymin = lowCITime,
    ymax = highCITime,
    color = targetLevel
  )
) +
  geom_pointrange(position = pd) 

m = aov(time_ave ~ targetLevel*targetKey, data=log_threeLevel_time) # make anova-type linear model
shapiro.test(residuals(m))
qqnorm(residuals(m)); qqline(residuals(m)) # Q-Q plot

library(ARTool)
log_threeLevel_time$id = factor(log_threeLevel_time$id) # Subject id must be nominal
m = art(time_ave ~ targetLevel*targetKey + (1|id), data=log_threeLevel_time) # subjects (S) as random effect
anova(m)

art.con(m, "targetLevel")
art.con(m, "targetKey")

log_threeLevel_time_summary_level <- log_threeLevel_time  %>%
  group_by(targetLevel) %>%
  summarize(
    meanTime = time_ave %>% mean(na.rm=TRUE),
    lowCITime = ci(time_ave)[2] %>% pmax(0),
    highCITime = ci(time_ave)[3],
    sdTime = ci(time_ave)[4],
    stdTime = sd(time_ave)) %>%
  ungroup() %>%
  arrange(targetLevel)

log_threeLevel_time_summary_level

# line + dot (levels)
threelevel_time_level <- ggplot(log_threeLevel_time_summary_level) +
  geom_pointrange( aes(x=reorder(targetLevel, desc(targetLevel)), y=meanTime, ymin=lowCITime, ymax=highCITime), colour="#707b7c", alpha=0.9, size=0.8) +
  scale_y_continuous(lim=c(900,1800)) + 
  coord_flip()

threelevel_time_level

threelevel_time_level + theme( # remove the vertical grid lines
          panel.background = element_blank(),
          panel.grid.major.y = element_blank() ,
          # explicitly set the horizontal lines (or they will disappear too)
          panel.grid.major.x = element_line( size=.1, color="gray" ),
          axis.title.x = element_blank(),
          axis.text.x=element_blank(),
          axis.ticks.x = element_blank(),
          axis.title.y = element_blank(),
          axis.text.y=element_blank(),
          axis.ticks.y = element_blank()
    )

ggsave("time_threelevel_level.pdf", width = 4, height = 3)


log_threeLevel_time_summary_key <- log_threeLevel_time  %>%
  group_by(targetKey) %>%
  summarize(
    meanTime = time_ave %>% mean(na.rm=TRUE),
    lowCITime = ci(time_ave)[2] %>% pmax(0),
    highCITime = ci(time_ave)[3],
    sdTime = ci(time_ave)[4],
    stdTime = sd(time_ave)) %>%
  ungroup() %>%
  arrange(targetKey)

log_threeLevel_time_summary_key

# line + dot (key)
threelevel_time_key <- ggplot(log_threeLevel_time_summary_key) +
  geom_pointrange( aes(x=reorder(targetKey, desc(targetKey)), y=meanTime, ymin=lowCITime, ymax=highCITime), colour="#707b7c", alpha=0.9, size=0.8) +
  scale_y_continuous(lim=c(900,1800)) + 
  coord_flip()

threelevel_time_key

threelevel_time_key + theme( # remove the vertical grid lines
          panel.background = element_blank(),
          panel.grid.major.y = element_blank() ,
          # explicitly set the horizontal lines (or they will disappear too)
          panel.grid.major.x = element_line( size=.1, color="gray" ),
          axis.title.x = element_blank(),
          axis.text.x=element_blank(),
          axis.ticks.x = element_blank(),
          axis.title.y = element_blank(),
          axis.text.y=element_blank(),
          axis.ticks.y = element_blank()
    )

ggsave("time_threelevel_key.pdf", width = 4, height = 8)
```

Main effect on targetLevel: full and light is faster than medium
Main effect on targetKey: (AS) faster than (DFJKL;), (DF;) faster than (KL), J faster than K

### 4 level

#### accuracy
```{r warning=FALSE}
log_fourlevel_accuracy <- trial_log %>%
  filter(levelCounts == c("4")) %>%
  group_by(id, targetLevel, targetKey) %>%
  summarize(
    accuracy_ave = sum(isSuccessful) / n(),
    n_trials = n()
  ) %>%
  ungroup() %>%
  arrange(id, targetLevel, targetKey)

log_fourlevel_accuracy_summary <- log_fourlevel_accuracy  %>%
  group_by(targetLevel, targetKey) %>%
  summarize(
    meanAccuracy = accuracy_ave %>% mean(na.rm=TRUE),
    lowCIAccuracy = ci(accuracy_ave)[2] %>% pmax(0),
    highCIAccuracy = ci(accuracy_ave)[3] %>% pmin(1),
    sdAccuracy = ci(accuracy_ave)[4],
    stdAccuracy = sd(accuracy_ave)) %>%
  ungroup() %>%
  arrange(targetLevel, targetKey)

log_fourlevel_accuracy_summary

pd <- position_dodge(width = 0.3)
log_fourlevel_accuracy_summary %>% ggplot(
  aes(
    x = targetKey,
    y = meanAccuracy,
    ymin = lowCIAccuracy,
    ymax = highCIAccuracy,
    color = targetLevel
  )
) +
  geom_pointrange(position = pd) 

m = aov(accuracy_ave ~ targetLevel*targetKey, data=log_fourlevel_accuracy) # make anova-type linear model
shapiro.test(residuals(m))
qqnorm(residuals(m)); qqline(residuals(m)) # Q-Q plot

library(ARTool)
log_fourlevel_accuracy$id = factor(log_fourlevel_accuracy$id) # Subject id must be nominal
m = art(accuracy_ave ~ targetLevel*targetKey + (1|id), data=log_fourlevel_accuracy) # subjects (S) as random effect
anova(m)

art.con(m, "targetLevel")
art.con(m, "targetKey")

log_fourlevel_accuracy_summary_level <- log_fourlevel_accuracy  %>%
  group_by(targetLevel) %>%
  summarize(
    meanAccuracy = accuracy_ave %>% mean(na.rm=TRUE),
    lowCIAccuracy = ci(accuracy_ave)[2] %>% pmax(0),
    highCIAccuracy = ci(accuracy_ave)[3] %>% pmin(1),
    sdAccuracy = ci(accuracy_ave)[4],
    stdAccuracy = sd(accuracy_ave)) %>%
  ungroup() %>%
  arrange(targetLevel)

log_fourlevel_accuracy_summary_level

# line + dot (levels)
fourlevel_accuracy_level <- ggplot(log_fourlevel_accuracy_summary_level) +
  geom_pointrange( aes(x=reorder(targetLevel, desc(targetLevel)), y=meanAccuracy, ymin=lowCIAccuracy, ymax=highCIAccuracy), colour="#28b463", alpha=0.9, size=0.8) +
  scale_y_reverse(lim=c(1.0,0.3)) + 
  coord_flip()

fourlevel_accuracy_level

fourlevel_accuracy_level + theme( # remove the vertical grid lines
          panel.background = element_blank(),
          panel.grid.major.y = element_blank() ,
          # explicitly set the horizontal lines (or they will disappear too)
          panel.grid.major.x = element_line( size=.1, color="gray" ),
          axis.title.x = element_blank(),
          axis.text.x=element_blank(),
          axis.ticks.x = element_blank(),
          axis.title.y = element_blank(),
          axis.text.y=element_blank(),
          axis.ticks.y = element_blank()
    )

ggsave("accuracy_fourlevel_level.pdf", width = 4, height = 4)

log_fourlevel_accuracy_summary_key <- log_fourlevel_accuracy  %>%
  group_by(targetKey) %>%
  summarize(
    meanAccuracy = accuracy_ave %>% mean(na.rm=TRUE),
    lowCIAccuracy = ci(accuracy_ave)[2] %>% pmax(0),
    highCIAccuracy = ci(accuracy_ave)[3] %>% pmin(1),
    sdAccuracy = ci(accuracy_ave)[4],
    stdAccuracy = sd(accuracy_ave)) %>%
  ungroup() %>%
  arrange(targetKey)

log_fourlevel_accuracy_summary_key

# line + dot (key)
fourlevel_accuracy_key <- ggplot(log_fourlevel_accuracy_summary_key) +
  geom_pointrange( aes(x=reorder(targetKey, desc(targetKey)), y=meanAccuracy, ymin=lowCIAccuracy, ymax=highCIAccuracy), colour="#28b463", alpha=0.9, size=0.8) +
  scale_y_reverse(lim=c(1.0,0.3)) + 
  coord_flip()

fourlevel_accuracy_key

fourlevel_accuracy_key + theme( # remove the vertical grid lines
          panel.background = element_blank(),
          panel.grid.major.y = element_blank() ,
          # explicitly set the horizontal lines (or they will disappear too)
          panel.grid.major.x = element_line( size=.1, color="gray" ),
          axis.title.x = element_blank(),
          axis.text.x=element_blank(),
          axis.ticks.x = element_blank(),
          axis.title.y = element_blank(),
          axis.text.y=element_blank(),
          axis.ticks.y = element_blank()
    )

ggsave("accuracy_fourlevel_key.pdf", width = 4, height = 8)

```

Main effect on targetLevel: Full has highest accuracy; MediumHigh has lowest accuracy; Light higher than MediumLow
Main effect on targetKey: J higher than ASDKL, F higher than L


#### actual press - user threshold
```{r warning=FALSE}
log_fourlevel <- trial_log %>%
  filter(levelCounts == c("4"))

log_fourlevel_user <- log_fourlevel %>% 
  group_by(id, targetLevel) %>% 
  mutate(
    pressRawPercent = pressedRaw * 100.0 / 255.0,
  ) %>% 
  ungroup()

log_fourlevel_user_quantile <- log_fourlevel_user%>%
  group_by(id, targetLevel) %>%
  summarize(
    lower_outlier = boxplot.stats(pressedRaw)$stats[c(1)],
    lower = boxplot.stats(pressedRaw)$stats[c(2)],
    median = boxplot.stats(pressedRaw)$stats[c(3)],
    upper = boxplot.stats(pressedRaw)$stats[c(4)],
    upper_outlier = boxplot.stats(pressedRaw)$stats[c(5)],
  ) %>%
  ungroup() %>%
  arrange(id, targetLevel)

library(reshape2) # for dcast

melted_threshold <- melt(log_fourlevel_user_quantile, id.vars = c("id", "targetLevel"), measure.vars = c("lower_outlier", "lower", "median", "upper", "upper_outlier"))
cast_threshold <- dcast(melted_threshold, id~targetLevel * variable, value.var="value") %>% 
  group_by(id) %>%
  mutate(
    full_threshold =  median(c(full_lower_outlier, full_lower,mediumHigh_upper, mediumHigh_upper_outlier)),
    mediumHigh_threshold =  median(c(mediumHigh_lower_outlier, mediumHigh_lower,mediumLow_upper, mediumLow_upper_outlier)),
    mediumLow_threshold =  median(c(mediumLow_lower_outlier, mediumLow_lower,light_upper, light_upper_outlier)),
  ) %>%
  ungroup()

log_fourlevel_user <- merge(log_fourlevel_user, cast_threshold,
                          by = 'id', all = TRUE)

log_fourlevel_user <- log_fourlevel_user %>% 
  mutate(
    pressLevel_user = ifelse(pressedRaw >= full_threshold, "full", ifelse(pressedRaw >= mediumHigh_threshold, "mediumHigh", ifelse(pressedRaw >= mediumLow_threshold, "mediumLow", "light"))),
    isSuccessful_user = (targetLevel == pressLevel_user)
  )


log_fourlevel_user %>% ggplot(
  aes(
    x = targetLevel,
    y = pressRawPercent
  )
) + 
  geom_violin() + 
  geom_boxplot(width = 0.03, outlier.shape = 1, , outlier.alpha = 0.3)

```


##### confusion table
```{r warning=FALSE}
library(cvms)
conf_mat <- confusion_matrix(targets = log_fourlevel_user$targetLevel,
                             predictions = log_fourlevel_user$pressedLevel)

conf_mat

plot_confusion_matrix(conf_mat$`Confusion Matrix`[[1]],
  add_normalized = FALSE,
  add_row_percentages = FALSE,
  class_order = c("full", "mediumHigh", "mediumLow", "light"))

conf_mat <- confusion_matrix(targets = log_fourlevel_user$targetLevel,
                             predictions = log_fourlevel_user$pressLevel_user)

conf_mat

plot_confusion_matrix(conf_mat$`Confusion Matrix`[[1]],
  add_normalized = FALSE,
  add_row_percentages = FALSE,
  class_order = c("full", "mediumHigh", "mediumLow", "light"))


```

#### time
```{r warning=FALSE}
log_fourLevel_time <- log_time_filtered%>%
  filter(levelCounts == c("4")) %>%
  group_by(id, targetLevel, targetKey) %>%
  summarize(
    time_ave = sum(time) / n(),
    n_trials = n()
  ) %>%
  ungroup() %>%
  arrange(id, targetLevel, targetKey)

log_fourLevel_time_summary <- log_fourLevel_time  %>%
  group_by(targetLevel, targetKey) %>%
  summarize(
    meanTime = time_ave %>% mean(na.rm=TRUE),
    lowCITime = ci(time_ave)[2] %>% pmax(0),
    highCITime = ci(time_ave)[3],
    sdTime = ci(time_ave)[4],
    stdTime = sd(time_ave)) %>%
  ungroup() %>%
  arrange(targetLevel, targetKey)

log_fourLevel_time_summary

pd <- position_dodge(width = 0.3)
log_fourLevel_time_summary %>% ggplot(
  aes(
    x = targetKey,
    y = meanTime,
    ymin = lowCITime,
    ymax = highCITime,
    color = targetLevel
  )
) +
  geom_pointrange(position = pd) 

m = aov(time_ave ~ targetLevel*targetKey, data=log_fourLevel_time) # make anova-type linear model
shapiro.test(residuals(m))
qqnorm(residuals(m)); qqline(residuals(m)) # Q-Q plot

library(ARTool)
log_fourLevel_time$id = factor(log_fourLevel_time$id) # Subject id must be nominal
m = art(time_ave ~ targetLevel*targetKey + (1|id), data=log_fourLevel_time) # subjects (S) as random effect
anova(m)

art.con(m, "targetLevel")
art.con(m, "targetKey")

log_fourLevel_time_summary_level <- log_fourLevel_time  %>%
  group_by(targetLevel) %>%
  summarize(
    meanTime = time_ave %>% mean(na.rm=TRUE),
    lowCITime = ci(time_ave)[2] %>% pmax(0),
    highCITime = ci(time_ave)[3],
    sdTime = ci(time_ave)[4],
    stdTime = sd(time_ave)) %>%
  ungroup() %>%
  arrange(targetLevel)

log_fourLevel_time_summary_level

# line + dot (levels)
fourlevel_time_level <- ggplot(log_fourLevel_time_summary_level) +
  geom_pointrange( aes(x=reorder(targetLevel, desc(targetLevel)), y=meanTime, ymin=lowCITime, ymax=highCITime), colour="#707b7c", alpha=0.9, size=0.8) +
  scale_y_continuous(lim=c(900,1800)) + 
  coord_flip()

fourlevel_time_level

fourlevel_time_level + theme( # remove the vertical grid lines
          panel.background = element_blank(),
          panel.grid.major.y = element_blank() ,
          # explicitly set the horizontal lines (or they will disappear too)
          panel.grid.major.x = element_line( size=.1, color="gray" ),
          axis.title.x = element_blank(),
          axis.text.x=element_blank(),
          axis.ticks.x = element_blank(),
          axis.title.y = element_blank(),
          axis.text.y=element_blank(),
          axis.ticks.y = element_blank()
    )

ggsave("time_fourlevel_level.pdf", width = 4, height = 4)


log_fourLevel_time_summary_key <- log_fourLevel_time  %>%
  group_by(targetKey) %>%
  summarize(
    meanTime = time_ave %>% mean(na.rm=TRUE),
    lowCITime = ci(time_ave)[2] %>% pmax(0),
    highCITime = ci(time_ave)[3],
    sdTime = ci(time_ave)[4],
    stdTime = sd(time_ave)) %>%
  ungroup() %>%
  arrange(targetKey)

log_fourLevel_time_summary_key

# line + dot (key)
fourlevel_time_key <- ggplot(log_fourLevel_time_summary_key) +
  geom_pointrange( aes(x=reorder(targetKey, desc(targetKey)), y=meanTime, ymin=lowCITime, ymax=highCITime), colour="#707b7c", alpha=0.9, size=0.8) +
  scale_y_continuous(lim=c(900,1800)) + 
  coord_flip()

fourlevel_time_key

fourlevel_time_key + theme( # remove the vertical grid lines
          panel.background = element_blank(),
          panel.grid.major.y = element_blank() ,
          # explicitly set the horizontal lines (or they will disappear too)
          panel.grid.major.x = element_line( size=.1, color="gray" ),
          axis.title.x = element_blank(),
          axis.text.x=element_blank(),
          axis.ticks.x = element_blank(),
          axis.title.y = element_blank(),
          axis.text.y=element_blank(),
          axis.ticks.y = element_blank()
    )

ggsave("time_fourlevel_key.pdf", width = 4, height = 8)
```

Main effect on targetLevel: (full, light) faster than (mediumHigh, mediumLow), mediumLow faster than mediumHigh
Main effect on targetKey: (AS) faster than (DFJKL;), (F;) faster than (KL), D faster than L


### Accuracy levelcount - user
```{r warning=FALSE}

log_fourlevel_user_accuracy <- log_fourlevel_user %>%
  dplyr::select(id:isSuccessful, pressLevel_user, isSuccessful_user)

log_threelevel_user_accuracy <- log_threelevel_user %>%
  dplyr::select(id:isSuccessful, pressLevel_user, isSuccessful_user)

log_twolevel_user_accuracy <- log_twolevel_user %>%
  dplyr::select(id:isSuccessful, pressLevel_user, isSuccessful_user)

log_user = bind_rows(log_twolevel_user_accuracy,log_threelevel_user_accuracy, log_fourlevel_user_accuracy)

log_defult_accuracy <- log_user %>%
  group_by(id, levelCounts) %>%
  summarize(
    accuracy_ave = sum(isSuccessful) / n(),
    n_trials = n()
  ) %>%
  mutate(
    method = "default"
  ) %>%
  ungroup() %>%
  arrange(id, levelCounts)
  
log_user_accuracy <- log_user %>%
  group_by(id, levelCounts) %>%
  summarize(
    accuracy_ave = sum(isSuccessful_user) / n(),
    n_trials = n()
  ) %>%
  mutate(
    method = "user"
  ) %>%
  ungroup() %>%
  arrange(id, levelCounts)
  
log_accuracy = bind_rows(log_defult_accuracy, log_user_accuracy)


log_accuracy_summary <- log_accuracy  %>%
  group_by(levelCounts, method) %>%
  summarize(
    meanAccuracy = accuracy_ave %>% mean(na.rm=TRUE),
    lowCIAccuracy = ci(accuracy_ave)[2] %>% pmax(0),
    highCIAccuracy = ci(accuracy_ave)[3] %>% pmin(1),
    sdAccuracy = ci(accuracy_ave)[4],
    stdAccuracy = sd(accuracy_ave)) %>%
  ungroup() %>%
  arrange(method, levelCounts)

log_accuracy_summary

pd <- position_dodge(width = 0.3)
log_accuracy_summary %>% ggplot(
  aes(
    x = levelCounts,
    y = meanAccuracy,
    ymin = lowCIAccuracy,
    ymax = highCIAccuracy,
    color = method
  )
) +
  geom_pointrange(position = pd) 
```