---
title: "trial results"
author: "Allen Yeh"
output:
  html_document: default
  pdf_document: default
---

```
```

```{r warning=FALSE}
library(tidyverse)
library(gmodels)
library(rstatix)
library(ggplot2)
library(ez)

#increase print limit to 2500 values
options(max.print=3000)
```

### Import data

#### Read the csv file and claim the data type
```{r}
 
participant_id = c("1", "2", "3", "4", "5", "6", "7", "8", "9", "10", "11", "12", "13", "14", "15", "16", "17", "18", "19", "20", "21", "23", "24", "40")

key_code = c("A", "S", "D", "F", "J", "K", "L", "Semicolon")

level_code = c("full", "mediumHigh", "mediumLow", "medium", "light")

# Initialize an empty data frame
trial_log = NULL

for (x in participant_id) {
  filename <- paste("./../results/", x, ".csv", sep="")
  trial_user_log <- read_csv(filename, col_types = cols(
    id = col_factor(levels = participant_id),
    level = col_integer(),
    block = col_factor(levels = c("0", "1", "2", "3", "4", "5")),
    trial = col_integer(),
    levelCounts = col_factor(levels = c("2", "3", "4")),
    targetKey = col_factor(levels = key_code),
    targetLevel = col_factor(levels = level_code),
    pressedLevel = col_factor(levels = level_code),
    pressedRaw = col_integer(),
    isSuccessful = col_logical(),
    startTime = col_double(),
    endTime = col_double(),
    time = col_double(),
  )) %>% filter(block %in% c("1", "2", "3", "4", "5"))
  trial_log = bind_rows(trial_log,trial_user_log)
}


```

### functions

```{r warning=FALSE}
percent <- function(num, digits = 2, ...) {      
  percentage <-formatC(num * 100, format = "f", digits = digits, ...)
  
  # appending "%" symbol at the end of
  # calculate percentage value
  paste0(percentage, "%")
}

INT <- function(x){
    qnorm((rank(x) - 0.5)/length(x))
}
```

### Filter outlier with time
```{r warning = FALSE}
trial_log_filtered <- trial_log %>% 
  group_by(id, levelCounts) %>% 
  mutate(IQR = IQR(time),
            O_upper = quantile(time, probs=c( .75), na.rm = FALSE)+1.5*IQR,  
            O_lower = quantile(time, probs=c( .25), na.rm = FALSE)-1.5*IQR  
  ) %>% 
  filter(O_lower <= time & time <= O_upper)%>% 
  ungroup()
```

Total 437 trials (5.1%) got removed.

### Total

#### block accuracy
```{r warning=FALSE}

log_block_accuracy <- trial_log_filtered %>%
  group_by(id, levelCounts, block) %>%
  summarize(
    accuracy_ave = sum(isSuccessful) / n(),
    n_trials = n()
  ) %>%
  ungroup() %>%
  arrange(id, levelCounts, block)

log_accuracy_summary <- log_block_accuracy  %>%
  group_by(block, levelCounts) %>%
  summarize(
    meanAccuracy = accuracy_ave %>% mean(na.rm=TRUE),
    lowCIAccuracy = ci(accuracy_ave)[2] %>% pmax(0),
    highCIAccuracy = ci(accuracy_ave)[3] %>% pmin(1),
    sdAccuracy = ci(accuracy_ave)[4],
    stdAccuracy = sd(accuracy_ave)) %>%
  ungroup() %>%
  arrange(block, levelCounts)

log_accuracy_summary

pd <- position_dodge(width = 0.3)
log_accuracy_summary %>% ggplot(
  aes(
    x = block,
    y = meanAccuracy,
    ymin = lowCIAccuracy,
    ymax = highCIAccuracy,
    color = levelCounts
  )
) +
  geom_pointrange(position = pd) 

m = aov(accuracy_ave ~ block*levelCounts, data=log_block_accuracy) # make anova-type linear model
shapiro.test(residuals(m))
qqnorm(residuals(m)); qqline(residuals(m)) # Q-Q plot

library(ez) # for ezANOVA
log_block_accuracy$id = factor(log_block_accuracy$id)
m = ezANOVA(dv=accuracy_ave, within=c(block, levelCounts), wid=id, data=log_block_accuracy)
m$Mauchly # p<.05 indicates a sphericity violation
m$ANOVA # use if no violation

pairwise.t.test(log_block_accuracy$accuracy_ave, log_block_accuracy$block, paired=TRUE, p.adjust="holm")

```

Effect on block, pairwise only showed the difference between block 1 and 4. Remove block 1 for following test.


#### levelCount accuracy
```{r warning=FALSE}
trial_log_filtered <- trial_log_filtered %>%
  filter(block != c("1"))

log_accuracy <- trial_log_filtered %>%
  group_by(id, levelCounts) %>%
  summarize(
    accuracy_ave = sum(isSuccessful) / n(),
    n_trials = n()
  ) %>%
  ungroup() %>%
  arrange(id, levelCounts)

log_accuracy_summary <- log_accuracy  %>%
  group_by(levelCounts) %>%
  summarize(
    meanAccuracy = accuracy_ave %>% mean(na.rm=TRUE),
    lowCIAccuracy = ci(accuracy_ave)[2] %>% pmax(0),
    highCIAccuracy = ci(accuracy_ave)[3] %>% pmin(1),
    sdAccuracy = ci(accuracy_ave)[4],
    stdAccuracy = sd(accuracy_ave)) %>%
  ungroup() %>%
  arrange(levelCounts)

log_accuracy_summary

# pd <- position_dodge(width = 0.3)
# log_accuracy_summary %>% ggplot(
#   aes(
#     x = levelCounts,
#     y = meanAccuracy,
#     ymin = lowCIAccuracy,
#     ymax = highCIAccuracy
#   )
# ) +
#   geom_pointrange(position = pd) 

# line + dot
accuracy_graph <- ggplot(log_accuracy_summary) +
  geom_pointrange( aes(x=reorder(levelCounts, desc(levelCounts)), y=meanAccuracy, ymin=lowCIAccuracy, ymax=highCIAccuracy), colour="#28b463", alpha=0.9, size=0.8) +
  scale_y_reverse(lim=c(1.0,0.3)) + 
  coord_flip()

accuracy_graph

accuracy_graph + theme( # remove the vertical grid lines
          panel.background = element_blank(),
          panel.grid.major.y = element_blank() ,
          # explicitly set the horizontal lines (or they will disappear too)
          panel.grid.major.x = element_line( size=.1, color="gray" ),
          axis.title.x = element_blank(),
          axis.text.x=element_blank(),
          axis.ticks.x = element_blank(),
          axis.title.y = element_blank(),
          axis.text.y=element_blank(),
          axis.ticks.y = element_blank()
    )

ggsave("accuracy_levels.pdf", width = 4, height = 3)



```


##### levelCount accuracy analysis
```{r warning=FALSE}
m = aov(accuracy_ave ~ levelCounts, data=log_accuracy) # make anova-type linear model
shapiro.test(residuals(m))
qqnorm(residuals(m)); qqline(residuals(m)) # Q-Q plot

library(ez) # for ezANOVA
log_accuracy$id = factor(log_accuracy$id)
m = ezANOVA(dv=accuracy_ave, within=c(levelCounts), wid=id, data=log_accuracy)
m$Mauchly # p<.05 indicates a sphericity violation
m$ANOVA # use if no violation

pairwise.t.test(log_accuracy$accuracy_ave, log_accuracy$levelCounts, paired=TRUE, p.adjust="holm")
```

2 levels is better than 3 and 4 levels. 
3 levels is better than 4 levels.


#### levelCount time
```{r warning=FALSE}


log_time <- trial_log_filtered %>%
  group_by(id, levelCounts) %>%
  summarize(
    time_ave = sum(time) / n(),
    n_trials = n()
  ) %>%
  ungroup() %>%
  arrange(id, levelCounts)

log_time_summary <- log_time  %>%
  group_by(levelCounts) %>%
  summarize(
    meanTime = time_ave %>% mean(na.rm=TRUE),
    lowCITime = ci(time_ave)[2] %>% pmax(0),
    highCITime = ci(time_ave)[3],
    sdTime = ci(time_ave)[4],
    stdTime = sd(time_ave)) %>%
  ungroup() %>%
  arrange(levelCounts)

log_time_summary

# pd <- position_dodge(width = 0.3)
# log_time_summary %>% ggplot(
#   aes(
#     x = levelCounts,
#     y = meanTime,
#     ymin = lowCITime,
#     ymax = highCITime
#   )
# ) +
#   geom_pointrange(position = pd) 

# line + dot
time_graph <- ggplot(log_time_summary) +
  geom_pointrange( aes(x=reorder(levelCounts, desc(levelCounts)), y=meanTime, ymin=lowCITime, ymax=highCITime), colour="#707b7c", alpha=0.9, size=0.8) +
  scale_y_continuous(lim=c(900,1850)) + 
  coord_flip()

time_graph

time_graph + theme( # remove the vertical grid lines
          panel.background = element_blank(),
          panel.grid.major.y = element_blank() ,
          # explicitly set the horizontal lines (or they will disappear too)
          panel.grid.major.x = element_line( size=.1, color="gray" ),
          axis.title.x = element_blank(),
          axis.text.x=element_blank(),
          axis.ticks.x = element_blank(),
          axis.title.y = element_blank(),
          axis.text.y=element_blank(),
          axis.ticks.y = element_blank()
    )

ggsave("time_levels.pdf", width = 4, height = 3)


```


##### levelCount time analysis
```{r warning=FALSE}
m = aov(time_ave ~ levelCounts, data=log_time) # make anova-type linear model
shapiro.test(residuals(m))
qqnorm(residuals(m)); qqline(residuals(m)) # Q-Q plot

library(rcompanion)
log_time$time_ave_trans = transformTukey(log_time$time_ave)

m = aov(time_ave_trans ~ levelCounts, data=log_time) # make anova-type linear model
shapiro.test(residuals(m))
qqnorm(residuals(m)); qqline(residuals(m)) # Q-Q plot

library(ez) # for ezANOVA
log_time$id = factor(log_time$id)
m = ezANOVA(dv=time_ave_trans, within=c(levelCounts), wid=id, data=log_time)
m$Mauchly # p<.05 indicates a sphericity violation
m$ANOVA # use if no violation

pairwise.t.test(log_time$time_ave_trans, log_time$levelCounts, paired=TRUE, p.adjust="holm")
```

Using tucky for normalization. 
2 levels is faster than 3 and 4 levels. 
3 levels is faster than 4 levels.


### 2 level

#### accuracy
```{r warning=FALSE}
log_twolevel_accuracy <- trial_log_filtered %>%
  filter(levelCounts == c("2")) %>%
  group_by(id, targetLevel, targetKey) %>%
  summarize(
    accuracy_ave = sum(isSuccessful) / n(),
    n_trials = n()
  ) %>%
  ungroup() %>%
  arrange(id, targetLevel, targetKey)

log_twolevel_accuracy_summary <- log_twolevel_accuracy  %>%
  group_by(targetLevel, targetKey) %>%
  summarize(
    meanAccuracy = accuracy_ave %>% mean(na.rm=TRUE),
    lowCIAccuracy = ci(accuracy_ave)[2] %>% pmax(0),
    highCIAccuracy = ci(accuracy_ave)[3] %>% pmin(1),
    sdAccuracy = ci(accuracy_ave)[4],
    stdAccuracy = sd(accuracy_ave)) %>%
  ungroup() %>%
  arrange(targetLevel, targetKey)

log_twolevel_accuracy_summary

pd <- position_dodge(width = 0.3)
log_twolevel_accuracy_summary %>% ggplot(
  aes(
    x = targetKey,
    y = meanAccuracy,
    ymin = lowCIAccuracy,
    ymax = highCIAccuracy,
    color = targetLevel
  )
) +
  geom_pointrange(position = pd) 


log_twolevel_accuracy_summary_level <- log_twolevel_accuracy  %>%
  group_by(targetLevel) %>%
  summarize(
    meanAccuracy = accuracy_ave %>% mean(na.rm=TRUE),
    lowCIAccuracy = ci(accuracy_ave)[2] %>% pmax(0),
    highCIAccuracy = ci(accuracy_ave)[3] %>% pmin(1),
    sdAccuracy = ci(accuracy_ave)[4],
    stdAccuracy = sd(accuracy_ave)) %>%
  ungroup() %>%
  arrange(targetLevel)

log_twolevel_accuracy_summary_level

# line + dot (levels)
twolevel_accuracy_level <- ggplot(log_twolevel_accuracy_summary_level) +
  geom_pointrange( aes(x=reorder(targetLevel, desc(targetLevel)), y=meanAccuracy, ymin=lowCIAccuracy, ymax=highCIAccuracy), colour="#28b463", alpha=0.9, size=0.8) +
  scale_y_reverse(lim=c(1.0,0.3)) + 
  coord_flip()

twolevel_accuracy_level

twolevel_accuracy_level + theme( # remove the vertical grid lines
          panel.background = element_blank(),
          panel.grid.major.y = element_blank() ,
          # explicitly set the horizontal lines (or they will disappear too)
          panel.grid.major.x = element_line( size=.1, color="gray" ),
          axis.title.x = element_blank(),
          axis.text.x=element_blank(),
          axis.ticks.x = element_blank(),
          axis.title.y = element_blank(),
          axis.text.y=element_blank(),
          axis.ticks.y = element_blank()
    )

ggsave("2level_accuracy_level.pdf", width = 4, height = 2)

log_twolevel_accuracy_summary_key <- log_twolevel_accuracy  %>%
  group_by(targetKey) %>%
  summarize(
    meanAccuracy = accuracy_ave %>% mean(na.rm=TRUE),
    lowCIAccuracy = ci(accuracy_ave)[2] %>% pmax(0),
    highCIAccuracy = ci(accuracy_ave)[3] %>% pmin(1),
    sdAccuracy = ci(accuracy_ave)[4],
    stdAccuracy = sd(accuracy_ave)) %>%
  ungroup() %>%
  arrange(targetKey)

log_twolevel_accuracy_summary_key

# line + dot (key)
twolevel_accuracy_key <- ggplot(log_twolevel_accuracy_summary_key) +
  geom_pointrange( aes(x=reorder(targetKey, desc(targetKey)), y=meanAccuracy, ymin=lowCIAccuracy, ymax=highCIAccuracy), colour="#28b463", alpha=0.9, size=0.8) +
  scale_y_reverse(lim=c(1.0,0.3)) + 
  coord_flip()

twolevel_accuracy_key

twolevel_accuracy_key + theme( # remove the vertical grid lines
          panel.background = element_blank(),
          panel.grid.major.y = element_blank() ,
          # explicitly set the horizontal lines (or they will disappear too)
          panel.grid.major.x = element_line( size=.1, color="gray" ),
          axis.title.x = element_blank(),
          axis.text.x=element_blank(),
          axis.ticks.x = element_blank(),
          axis.title.y = element_blank(),
          axis.text.y=element_blank(),
          axis.ticks.y = element_blank()
    )

ggsave("2level_accuracy_key.pdf", width = 4, height = 8)
```


##### accuracy analysis
```{r warning=FALSE}
m = aov(accuracy_ave ~ targetLevel*targetKey, data=log_twolevel_accuracy) # make anova-type linear model
shapiro.test(residuals(m))
qqnorm(residuals(m)); qqline(residuals(m)) # Q-Q plot

plotNormalHistogram(log_twolevel_accuracy$accuracy_ave)
# 
# library(ez) # for ezANOVA
# log_twolevel_accuracy$id = factor(log_twolevel_accuracy$id)
# m = ezANOVA(dv=accuracy_ave, within=c(targetLevel,targetKey), wid=id, data=log_twolevel_accuracy)
# m$Mauchly # p<.05 indicates a sphericity violation
# m$ANOVA # use if no violation


library(lme4)
library(lmerTest)
library(car)

log_twolevel_accuracy$id = factor(log_twolevel_accuracy$id)
contrasts(log_twolevel_accuracy$targetLevel) <-"contr.sum"
contrasts(log_twolevel_accuracy$targetKey) <-"contr.sum"
m = glmer(accuracy_ave ~ targetLevel*targetKey + (1|id), data=log_twolevel_accuracy, family=poisson)
# use family=quasipoissonif overdispersion
Anova(m, type=3)

```

No effect.


#### time
```{r warning=FALSE}
log_twoLevel_time <- trial_log_filtered%>%
  filter(levelCounts == c("2")) %>%
  group_by(id, targetLevel, targetKey) %>%
  summarize(
    time_ave = sum(time) / n(),
    n_trials = n()
  ) %>%
  ungroup() %>%
  arrange(id, targetLevel, targetKey)

log_twoLevel_time_summary <- log_twoLevel_time  %>%
  group_by(targetLevel, targetKey) %>%
  summarize(
    meanTime = time_ave %>% mean(na.rm=TRUE),
    lowCITime = ci(time_ave)[2] %>% pmax(0),
    highCITime = ci(time_ave)[3],
    sdTime = ci(time_ave)[4],
    stdTime = sd(time_ave)) %>%
  ungroup() %>%
  arrange(targetLevel, targetKey)

log_twoLevel_time_summary

pd <- position_dodge(width = 0.3)
log_twoLevel_time_summary %>% ggplot(
  aes(
    x = targetKey,
    y = meanTime,
    ymin = lowCITime,
    ymax = highCITime,
    color = targetLevel
  )
) +
  geom_pointrange(position = pd) 


log_twoLevel_time_summary_level <- log_twoLevel_time  %>%
  group_by(targetLevel) %>%
  summarize(
    meanTime = time_ave %>% mean(na.rm=TRUE),
    lowCITime = ci(time_ave)[2] %>% pmax(0),
    highCITime = ci(time_ave)[3],
    sdTime = ci(time_ave)[4],
    stdTime = sd(time_ave)) %>%
  ungroup() %>%
  arrange(targetLevel)

log_twoLevel_time_summary_level

# line + dot (levels)
twolevel_time_level <- ggplot(log_twoLevel_time_summary_level) +
  geom_pointrange( aes(x=reorder(targetLevel, desc(targetLevel)), y=meanTime, ymin=lowCITime, ymax=highCITime), colour="#707b7c", alpha=0.9, size=0.8) +
  scale_y_continuous(lim=c(900,1850)) + 
  coord_flip()

twolevel_time_level

twolevel_time_level + theme( # remove the vertical grid lines
          panel.background = element_blank(),
          panel.grid.major.y = element_blank() ,
          # explicitly set the horizontal lines (or they will disappear too)
          panel.grid.major.x = element_line( size=.1, color="gray" ),
          axis.title.x = element_blank(),
          axis.text.x=element_blank(),
          axis.ticks.x = element_blank(),
          axis.title.y = element_blank(),
          axis.text.y=element_blank(),
          axis.ticks.y = element_blank()
    )

ggsave("2level_time_level.pdf", width = 4, height = 2)

log_twoLevel_time_summary_key <- log_twoLevel_time  %>%
  group_by(targetKey) %>%
  summarize(
    meanTime = time_ave %>% mean(na.rm=TRUE),
    lowCITime = ci(time_ave)[2] %>% pmax(0),
    highCITime = ci(time_ave)[3],
    sdTime = ci(time_ave)[4],
    stdTime = sd(time_ave)) %>%
  ungroup() %>%
  arrange(targetKey)

log_twoLevel_time_summary_key

# line + dot (key)
twolevel_time_key <- ggplot(log_twoLevel_time_summary_key) +
  geom_pointrange( aes(x=reorder(targetKey, desc(targetKey)), y=meanTime, ymin=lowCITime, ymax=highCITime), colour="#707b7c", alpha=0.9, size=0.8) +
  scale_y_continuous(lim=c(900,1850)) + 
  coord_flip()

twolevel_time_key

twolevel_time_key + theme( # remove the vertical grid lines
          panel.background = element_blank(),
          panel.grid.major.y = element_blank() ,
          # explicitly set the horizontal lines (or they will disappear too)
          panel.grid.major.x = element_line( size=.1, color="gray" ),
          axis.title.x = element_blank(),
          axis.text.x=element_blank(),
          axis.ticks.x = element_blank(),
          axis.title.y = element_blank(),
          axis.text.y=element_blank(),
          axis.ticks.y = element_blank()
    )

ggsave("2level_time_key.pdf", width = 4, height = 8)
```

##### time analysis
```{r warning=FALSE}
m = aov(time_ave ~ targetLevel*targetKey, data=log_twoLevel_time) # make anova-type linear model
shapiro.test(residuals(m))
qqnorm(residuals(m)); qqline(residuals(m)) # Q-Q plot

library(rcompanion)
log_twoLevel_time$time_ave_trans = transformTukey(log_twoLevel_time$time_ave)

m = aov(time_ave_trans ~ targetLevel*targetKey, data=log_twoLevel_time) # make anova-type linear model
shapiro.test(residuals(m))
qqnorm(residuals(m)); qqline(residuals(m)) # Q-Q plot

library(ez) # for ezANOVA
log_twoLevel_time$id = factor(log_twoLevel_time$id)
m = ezANOVA(dv=time_ave_trans, within=c(targetLevel,targetKey), wid=id, data=log_twoLevel_time, return_aov = TRUE)
m$Mauchly # p<.05 indicates a sphericity violation
m$ANOVA # use if no violation

pairwise.t.test(log_twoLevel_time$time_ave_trans, log_twoLevel_time$targetKey, paired=TRUE, p.adjust="holm")
```

Main effect on keys: A faster than SDFJKL;, SF; faster than KL, D faster than K


### 3 level

#### accuracy
```{r warning=FALSE}
log_threelevel_accuracy <- trial_log_filtered %>%
  filter(levelCounts == c("3")) %>%
  group_by(id, targetLevel, targetKey) %>%
  summarize(
    accuracy_ave = sum(isSuccessful) / n(),
    n_trials = n()
  ) %>%
  ungroup() %>%
  arrange(id, targetLevel, targetKey)

log_threelevel_accuracy_summary <- log_threelevel_accuracy  %>%
  group_by(targetLevel, targetKey) %>%
  summarize(
    meanAccuracy = accuracy_ave %>% mean(na.rm=TRUE),
    lowCIAccuracy = ci(accuracy_ave)[2] %>% pmax(0),
    highCIAccuracy = ci(accuracy_ave)[3] %>% pmin(1),
    sdAccuracy = ci(accuracy_ave)[4],
    stdAccuracy = sd(accuracy_ave)) %>%
  ungroup() %>%
  arrange(targetLevel, targetKey)

log_threelevel_accuracy_summary

pd <- position_dodge(width = 0.3)
log_threelevel_accuracy_summary %>% ggplot(
  aes(
    x = targetKey,
    y = meanAccuracy,
    ymin = lowCIAccuracy,
    ymax = highCIAccuracy,
    color = targetLevel
  )
) +
  geom_pointrange(position = pd) 


log_threelevel_accuracy_summary_level <- log_threelevel_accuracy  %>%
  group_by(targetLevel) %>%
  summarize(
    meanAccuracy = accuracy_ave %>% mean(na.rm=TRUE),
    lowCIAccuracy = ci(accuracy_ave)[2] %>% pmax(0),
    highCIAccuracy = ci(accuracy_ave)[3] %>% pmin(1),
    sdAccuracy = ci(accuracy_ave)[4],
    stdAccuracy = sd(accuracy_ave)) %>%
  ungroup() %>%
  arrange(targetLevel)

log_threelevel_accuracy_summary_level

# line + dot (levels)
threelevel_accuracy_level <- ggplot(log_threelevel_accuracy_summary_level) +
  geom_pointrange( aes(x=reorder(targetLevel, desc(targetLevel)), y=meanAccuracy, ymin=lowCIAccuracy, ymax=highCIAccuracy), colour="#28b463", alpha=0.9, size=0.8) +
  scale_y_reverse(lim=c(1.0,0.3)) + 
  coord_flip()

threelevel_accuracy_level

threelevel_accuracy_level + theme( # remove the vertical grid lines
          panel.background = element_blank(),
          panel.grid.major.y = element_blank() ,
          # explicitly set the horizontal lines (or they will disappear too)
          panel.grid.major.x = element_line( size=.1, color="gray" ),
          axis.title.x = element_blank(),
          axis.text.x=element_blank(),
          axis.ticks.x = element_blank(),
          axis.title.y = element_blank(),
          axis.text.y=element_blank(),
          axis.ticks.y = element_blank()
    )

ggsave("3level_accuracy_level.pdf", width = 4, height = 3)

log_threelevel_accuracy_summary_key <- log_threelevel_accuracy  %>%
  group_by(targetKey) %>%
  summarize(
    meanAccuracy = accuracy_ave %>% mean(na.rm=TRUE),
    lowCIAccuracy = ci(accuracy_ave)[2] %>% pmax(0),
    highCIAccuracy = ci(accuracy_ave)[3] %>% pmin(1),
    sdAccuracy = ci(accuracy_ave)[4],
    stdAccuracy = sd(accuracy_ave)) %>%
  ungroup() %>%
  arrange(targetKey)

log_threelevel_accuracy_summary_key

# line + dot (key)
threelevel_accuracy_key <- ggplot(log_threelevel_accuracy_summary_key) +
  geom_pointrange( aes(x=reorder(targetKey, desc(targetKey)), y=meanAccuracy, ymin=lowCIAccuracy, ymax=highCIAccuracy), colour="#28b463", alpha=0.9, size=0.8) +
  scale_y_reverse(lim=c(1.0,0.3)) + 
  coord_flip()

threelevel_accuracy_key

threelevel_accuracy_key + theme( # remove the vertical grid lines
          panel.background = element_blank(),
          panel.grid.major.y = element_blank() ,
          # explicitly set the horizontal lines (or they will disappear too)
          panel.grid.major.x = element_line( size=.1, color="gray" ),
          axis.title.x = element_blank(),
          axis.text.x=element_blank(),
          axis.ticks.x = element_blank(),
          axis.title.y = element_blank(),
          axis.text.y=element_blank(),
          axis.ticks.y = element_blank()
    )

ggsave("3level_accuracy_key.pdf", width = 4, height = 8)
```



#### accuracy analysis
```{r warning=FALSE}
m = aov(accuracy_ave ~ targetLevel*targetKey, data=log_threelevel_accuracy) # make anova-type linear model
shapiro.test(residuals(m))
qqnorm(residuals(m)); qqline(residuals(m)) # Q-Q plot

plotNormalHistogram(log_threelevel_accuracy$accuracy_ave)

library(lme4)
library(lmerTest)
library(car)

log_threelevel_accuracy$id = factor(log_threelevel_accuracy$id)
contrasts(log_threelevel_accuracy$targetLevel) <-"contr.sum"
contrasts(log_threelevel_accuracy$targetKey) <-"contr.sum"
m = glmer(accuracy_ave ~ targetLevel*targetKey + (1|id), data=log_threelevel_accuracy, family=poisson)
# use family=quasipoissonif overdispersion
Anova(m, type=3)

library(multcomp) # for glht
library(emmeans) # for emm, emmeans
summary(glht(m, emm(pairwise ~ targetLevel)), test=adjusted(type="holm"))

```
Main effect on targetLevel: Full has higher accuracy then medium and light; Medium has higher accuracy then light.


#### time
```{r warning=FALSE}
log_threeLevel_time <- trial_log_filtered%>%
  filter(levelCounts == c("3")) %>%
  group_by(id, targetLevel, targetKey) %>%
  summarize(
    time_ave = sum(time) / n(),
    n_trials = n()
  ) %>%
  ungroup() %>%
  arrange(id, targetLevel, targetKey)

log_threeLevel_time_summary <- log_threeLevel_time  %>%
  group_by(targetLevel, targetKey) %>%
  summarize(
    meanTime = time_ave %>% mean(na.rm=TRUE),
    lowCITime = ci(time_ave)[2] %>% pmax(0),
    highCITime = ci(time_ave)[3],
    sdTime = ci(time_ave)[4],
    stdTime = sd(time_ave)) %>%
  ungroup() %>%
  arrange(targetLevel, targetKey)

log_threeLevel_time_summary

pd <- position_dodge(width = 0.3)
log_threeLevel_time_summary %>% ggplot(
  aes(
    x = targetKey,
    y = meanTime,
    ymin = lowCITime,
    ymax = highCITime,
    color = targetLevel
  )
) +
  geom_pointrange(position = pd) 


log_threeLevel_time_summary_level <- log_threeLevel_time  %>%
  group_by(targetLevel) %>%
  summarize(
    meanTime = time_ave %>% mean(na.rm=TRUE),
    lowCITime = ci(time_ave)[2] %>% pmax(0),
    highCITime = ci(time_ave)[3],
    sdTime = ci(time_ave)[4],
    stdTime = sd(time_ave)) %>%
  ungroup() %>%
  arrange(targetLevel)

log_threeLevel_time_summary_level

# line + dot (levels)
threelevel_time_level <- ggplot(log_threeLevel_time_summary_level) +
  geom_pointrange( aes(x=reorder(targetLevel, desc(targetLevel)), y=meanTime, ymin=lowCITime, ymax=highCITime), colour="#707b7c", alpha=0.9, size=0.8) +
  scale_y_continuous(lim=c(900,1850)) + 
  coord_flip()

threelevel_time_level

threelevel_time_level + theme( # remove the vertical grid lines
          panel.background = element_blank(),
          panel.grid.major.y = element_blank() ,
          # explicitly set the horizontal lines (or they will disappear too)
          panel.grid.major.x = element_line( size=.1, color="gray" ),
          axis.title.x = element_blank(),
          axis.text.x=element_blank(),
          axis.ticks.x = element_blank(),
          axis.title.y = element_blank(),
          axis.text.y=element_blank(),
          axis.ticks.y = element_blank()
    )

ggsave("3level_time_level.pdf", width = 4, height = 3)


log_threeLevel_time_summary_key <- log_threeLevel_time  %>%
  group_by(targetKey) %>%
  summarize(
    meanTime = time_ave %>% mean(na.rm=TRUE),
    lowCITime = ci(time_ave)[2] %>% pmax(0),
    highCITime = ci(time_ave)[3],
    sdTime = ci(time_ave)[4],
    stdTime = sd(time_ave)) %>%
  ungroup() %>%
  arrange(targetKey)

log_threeLevel_time_summary_key

# line + dot (key)
threelevel_time_key <- ggplot(log_threeLevel_time_summary_key) +
  geom_pointrange( aes(x=reorder(targetKey, desc(targetKey)), y=meanTime, ymin=lowCITime, ymax=highCITime), colour="#707b7c", alpha=0.9, size=0.8) +
  scale_y_continuous(lim=c(900,1850)) + 
  coord_flip()

threelevel_time_key

threelevel_time_key + theme( # remove the vertical grid lines
          panel.background = element_blank(),
          panel.grid.major.y = element_blank() ,
          # explicitly set the horizontal lines (or they will disappear too)
          panel.grid.major.x = element_line( size=.1, color="gray" ),
          axis.title.x = element_blank(),
          axis.text.x=element_blank(),
          axis.ticks.x = element_blank(),
          axis.title.y = element_blank(),
          axis.text.y=element_blank(),
          axis.ticks.y = element_blank()
    )

ggsave("3level_time_key.pdf", width = 4, height = 8)
```


#### time
```{r warning=FALSE}
m = aov(time_ave ~ targetLevel*targetKey, data=log_threeLevel_time) # make anova-type linear model
shapiro.test(residuals(m))
qqnorm(residuals(m)); qqline(residuals(m)) # Q-Q plot

library(rcompanion)
log_threeLevel_time$time_ave_trans = transformTukey(log_threeLevel_time$time_ave)

m = aov(time_ave_trans ~ targetLevel*targetKey, data=log_threeLevel_time) # make anova-type linear model
shapiro.test(residuals(m))
qqnorm(residuals(m)); qqline(residuals(m)) # Q-Q plot

library(ez) # for ezANOVA
log_threeLevel_time$id = factor(log_threeLevel_time$id)
m = ezANOVA(dv=time_ave_trans, within=c(targetLevel,targetKey), wid=id, data=log_threeLevel_time)
m$Mauchly # p<.05 indicates a sphericity violation
m$Sphericity
m$ANOVA # use if no violation

pairwise.t.test(log_threeLevel_time$time_ave_trans, log_threeLevel_time$targetLevel, paired=TRUE, p.adjust="holm")
pairwise.t.test(log_threeLevel_time$time_ave_trans, log_threeLevel_time$targetKey, paired=TRUE, p.adjust="holm")
pairwise.t.test(log_threeLevel_time$time_ave_trans, interaction(log_threeLevel_time$targetKey, log_threeLevel_time$targetLevel), paired=TRUE, p.adjust="holm")

# library(ARTool)
# log_threeLevel_time$id = factor(log_threeLevel_time$id) # Subject id must be nominal
# m = art(time_ave ~ targetLevel*targetKey + (1|id), data=log_threeLevel_time) # subjects (S) as random effect
# anova(m)
# 
# art.con(m, "targetLevel")
# art.con(m, "targetKey")
# art.con(m, "targetLevel:targetKey")
```

Main effect on targetLevel: full and light is faster than medium

Main effect on targetKey: (AS) faster than (DFJKL;), (DF;) faster than (KL), J faster than K

Main interaction: For full, A faster than DKL

For medium, S faster than FJKL

For light, A faster than KL

### 4 level

#### accuracy
```{r warning=FALSE}
log_fourlevel_accuracy <- trial_log_filtered %>%
  filter(levelCounts == c("4")) %>%
  group_by(id, targetLevel, targetKey) %>%
  summarize(
    accuracy_ave = sum(isSuccessful) / n(),
    n_trials = n()
  ) %>%
  ungroup() %>%
  arrange(id, targetLevel, targetKey)

log_fourlevel_accuracy_summary <- log_fourlevel_accuracy  %>%
  group_by(targetLevel, targetKey) %>%
  summarize(
    meanAccuracy = accuracy_ave %>% mean(na.rm=TRUE),
    lowCIAccuracy = ci(accuracy_ave)[2] %>% pmax(0),
    highCIAccuracy = ci(accuracy_ave)[3] %>% pmin(1),
    sdAccuracy = ci(accuracy_ave)[4],
    stdAccuracy = sd(accuracy_ave)) %>%
  ungroup() %>%
  arrange(targetLevel, targetKey)

log_fourlevel_accuracy_summary

pd <- position_dodge(width = 0.3)
log_fourlevel_accuracy_summary %>% ggplot(
  aes(
    x = targetKey,
    y = meanAccuracy,
    ymin = lowCIAccuracy,
    ymax = highCIAccuracy,
    color = targetLevel
  )
) +
  geom_pointrange(position = pd) 



log_fourlevel_accuracy_summary_level <- log_fourlevel_accuracy  %>%
  group_by(targetLevel) %>%
  summarize(
    meanAccuracy = accuracy_ave %>% mean(na.rm=TRUE),
    lowCIAccuracy = ci(accuracy_ave)[2] %>% pmax(0),
    highCIAccuracy = ci(accuracy_ave)[3] %>% pmin(1),
    sdAccuracy = ci(accuracy_ave)[4],
    stdAccuracy = sd(accuracy_ave)) %>%
  ungroup() %>%
  arrange(targetLevel)

log_fourlevel_accuracy_summary_level

# line + dot (levels)
fourlevel_accuracy_level <- ggplot(log_fourlevel_accuracy_summary_level) +
  geom_pointrange( aes(x=reorder(targetLevel, desc(targetLevel)), y=meanAccuracy, ymin=lowCIAccuracy, ymax=highCIAccuracy), colour="#28b463", alpha=0.9, size=0.8) +
  scale_y_reverse(lim=c(1.0,0.3)) + 
  coord_flip()

fourlevel_accuracy_level

fourlevel_accuracy_level + theme( # remove the vertical grid lines
          panel.background = element_blank(),
          panel.grid.major.y = element_blank() ,
          # explicitly set the horizontal lines (or they will disappear too)
          panel.grid.major.x = element_line( size=.1, color="gray" ),
          axis.title.x = element_blank(),
          axis.text.x=element_blank(),
          axis.ticks.x = element_blank(),
          axis.title.y = element_blank(),
          axis.text.y=element_blank(),
          axis.ticks.y = element_blank()
    )

ggsave("4level_accuracy_level.pdf", width = 4, height = 4)

log_fourlevel_accuracy_summary_key <- log_fourlevel_accuracy  %>%
  group_by(targetKey) %>%
  summarize(
    meanAccuracy = accuracy_ave %>% mean(na.rm=TRUE),
    lowCIAccuracy = ci(accuracy_ave)[2] %>% pmax(0),
    highCIAccuracy = ci(accuracy_ave)[3] %>% pmin(1),
    sdAccuracy = ci(accuracy_ave)[4],
    stdAccuracy = sd(accuracy_ave)) %>%
  ungroup() %>%
  arrange(targetKey)

log_fourlevel_accuracy_summary_key

# line + dot (key)
fourlevel_accuracy_key <- ggplot(log_fourlevel_accuracy_summary_key) +
  geom_pointrange( aes(x=reorder(targetKey, desc(targetKey)), y=meanAccuracy, ymin=lowCIAccuracy, ymax=highCIAccuracy), colour="#28b463", alpha=0.9, size=0.8) +
  scale_y_reverse(lim=c(1.0,0.3)) + 
  coord_flip()

fourlevel_accuracy_key

fourlevel_accuracy_key + theme( # remove the vertical grid lines
          panel.background = element_blank(),
          panel.grid.major.y = element_blank() ,
          # explicitly set the horizontal lines (or they will disappear too)
          panel.grid.major.x = element_line( size=.1, color="gray" ),
          axis.title.x = element_blank(),
          axis.text.x=element_blank(),
          axis.ticks.x = element_blank(),
          axis.title.y = element_blank(),
          axis.text.y=element_blank(),
          axis.ticks.y = element_blank()
    )

ggsave("4level_accuracy_key.pdf", width = 4, height = 8)

```


##### accuracy analysis
```{r warning=FALSE}
m = aov(accuracy_ave ~ targetLevel*targetKey, data=log_fourlevel_accuracy) # make anova-type linear model
shapiro.test(residuals(m))
qqnorm(residuals(m)); qqline(residuals(m)) # Q-Q plot
plotNormalHistogram(log_fourlevel_accuracy$accuracy_ave)

library(lme4)
library(lmerTest)
library(car)

log_fourlevel_accuracy$id = factor(log_fourlevel_accuracy$id)
contrasts(log_fourlevel_accuracy$targetLevel) <-"contr.sum"
contrasts(log_fourlevel_accuracy$targetKey) <-"contr.sum"
m = glmer(accuracy_ave ~ targetLevel*targetKey + (1|id), data=log_fourlevel_accuracy, family=poisson)
# use family=quasipoissonif overdispersion
Anova(m, type=3)

library(multcomp) # for glht
library(emmeans) # for emm, emmeans
summary(glht(m, emm(pairwise ~ targetLevel)), test=adjusted(type="holm"))


# library(ARTool)
# log_fourlevel_accuracy$id = factor(log_fourlevel_accuracy$id) # Subject id must be nominal
# m = art(accuracy_ave ~ targetLevel*targetKey + (1|id), data=log_fourlevel_accuracy) # subjects (S) as random effect
# anova(m)
# 
# art.con(m, "targetLevel")
# art.con(m, "targetKey")
# art.con(m, "targetLevel:targetKey")
```
Main effect on targetLevel: Full has highest accuracy; MediumHigh has lowest accuracy


#### time
```{r warning=FALSE}
log_fourLevel_time <- trial_log_filtered%>%
  filter(levelCounts == c("4")) %>%
  group_by(id, targetLevel, targetKey) %>%
  summarize(
    time_ave = sum(time) / n(),
    n_trials = n()
  ) %>%
  ungroup() %>%
  arrange(id, targetLevel, targetKey)

log_fourLevel_time_summary <- log_fourLevel_time  %>%
  group_by(targetLevel, targetKey) %>%
  summarize(
    meanTime = time_ave %>% mean(na.rm=TRUE),
    lowCITime = ci(time_ave)[2] %>% pmax(0),
    highCITime = ci(time_ave)[3],
    sdTime = ci(time_ave)[4],
    stdTime = sd(time_ave)) %>%
  ungroup() %>%
  arrange(targetLevel, targetKey)

log_fourLevel_time_summary

pd <- position_dodge(width = 0.3)
log_fourLevel_time_summary %>% ggplot(
  aes(
    x = targetKey,
    y = meanTime,
    ymin = lowCITime,
    ymax = highCITime,
    color = targetLevel
  )
) +
  geom_pointrange(position = pd) 

log_fourLevel_time_summary_level <- log_fourLevel_time  %>%
  group_by(targetLevel) %>%
  summarize(
    meanTime = time_ave %>% mean(na.rm=TRUE),
    lowCITime = ci(time_ave)[2] %>% pmax(0),
    highCITime = ci(time_ave)[3],
    sdTime = ci(time_ave)[4],
    stdTime = sd(time_ave)) %>%
  ungroup() %>%
  arrange(targetLevel)

log_fourLevel_time_summary_level

# line + dot (levels)
fourlevel_time_level <- ggplot(log_fourLevel_time_summary_level) +
  geom_pointrange( aes(x=reorder(targetLevel, desc(targetLevel)), y=meanTime, ymin=lowCITime, ymax=highCITime), colour="#707b7c", alpha=0.9, size=0.8) +
  scale_y_continuous(lim=c(900,1850)) + 
  coord_flip()

fourlevel_time_level

fourlevel_time_level + theme( # remove the vertical grid lines
          panel.background = element_blank(),
          panel.grid.major.y = element_blank() ,
          # explicitly set the horizontal lines (or they will disappear too)
          panel.grid.major.x = element_line( size=.1, color="gray" ),
          axis.title.x = element_blank(),
          axis.text.x=element_blank(),
          axis.ticks.x = element_blank(),
          axis.title.y = element_blank(),
          axis.text.y=element_blank(),
          axis.ticks.y = element_blank()
    )

ggsave("4level_time_level.pdf", width = 4, height = 4)


log_fourLevel_time_summary_key <- log_fourLevel_time  %>%
  group_by(targetKey) %>%
  summarize(
    meanTime = time_ave %>% mean(na.rm=TRUE),
    lowCITime = ci(time_ave)[2] %>% pmax(0),
    highCITime = ci(time_ave)[3],
    sdTime = ci(time_ave)[4],
    stdTime = sd(time_ave)) %>%
  ungroup() %>%
  arrange(targetKey)

log_fourLevel_time_summary_key

# line + dot (key)
fourlevel_time_key <- ggplot(log_fourLevel_time_summary_key) +
  geom_pointrange( aes(x=reorder(targetKey, desc(targetKey)), y=meanTime, ymin=lowCITime, ymax=highCITime), colour="#707b7c", alpha=0.9, size=0.8) +
  scale_y_continuous(lim=c(900,1850)) + 
  coord_flip()

fourlevel_time_key

fourlevel_time_key + theme( # remove the vertical grid lines
          panel.background = element_blank(),
          panel.grid.major.y = element_blank() ,
          # explicitly set the horizontal lines (or they will disappear too)
          panel.grid.major.x = element_line( size=.1, color="gray" ),
          axis.title.x = element_blank(),
          axis.text.x=element_blank(),
          axis.ticks.x = element_blank(),
          axis.title.y = element_blank(),
          axis.text.y=element_blank(),
          axis.ticks.y = element_blank()
    )

ggsave("4level_time_key.pdf", width = 4, height = 8)
```


#### time analysis
```{r warning=FALSE}
m = aov(time_ave ~ targetLevel*targetKey, data=log_fourLevel_time) # make anova-type linear model
shapiro.test(residuals(m))
qqnorm(residuals(m)); qqline(residuals(m)) # Q-Q plot

library(rcompanion)
log_fourLevel_time$time_ave_trans = transformTukey(log_fourLevel_time$time_ave)

m = aov(time_ave_trans ~ targetLevel*targetKey, data=log_fourLevel_time) # make anova-type linear model
shapiro.test(residuals(m))
qqnorm(residuals(m)); qqline(residuals(m)) # Q-Q plot

library(ez) # for ezANOVA
log_fourLevel_time$id = factor(log_fourLevel_time$id)
m = ezANOVA(dv=time_ave_trans, within=c(targetLevel,targetKey), wid=id, data=log_fourLevel_time)
m$Mauchly # p<.05 indicates a sphericity violation
m$Sphericity
m$ANOVA # use if no violation

pairwise.t.test(log_fourLevel_time$time_ave_trans, log_fourLevel_time$targetLevel, paired=TRUE, p.adjust="holm")
pairwise.t.test(log_fourLevel_time$time_ave_trans, log_fourLevel_time$targetKey, paired=TRUE, p.adjust="holm")
pairwise.t.test(log_fourLevel_time$time_ave_trans, interaction(log_fourLevel_time$targetKey, log_fourLevel_time$targetLevel), paired=TRUE, p.adjust="holm")


# library(ARTool)
# log_fourLevel_time$id = factor(log_fourLevel_time$id) # Subject id must be nominal
# m = art(time_ave ~ targetLevel*targetKey + (1|id), data=log_fourLevel_time) # subjects (S) as random effect
# anova(m)
# 
# art.con(m, "targetLevel")
# art.con(m, "targetKey")
# art.con(m, "targetLevel:targetKey")
```
Main effect on targetLevel: all pairs have difference 

Main effect on targetKey: (AS) faster than (DFJKL;), (DF;) faster than (L), F faster than JK

Main interaction: for Full, ASF is faster than KL, A is faster than D

for Light, AS is faster than KL, F; is faster than L 

